### 2020-04-13 inst/doc/ms-perks-features.Rmd
version 1.0.2

---
title: "modelStudio - perks and features"
author: "Hubert Baniecki"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{modelStudio - perks and features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces an interactive, customizable dashboard made with D3.js. It consists of multiple panels for plots with their short descriptions. Easily save and share the dashboard with others. Tools for model exploration unite with tools for EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.

Let's use `HR` dataset to explore `modelStudio` parameters:

```{r results="hide"}
train <- DALEX::HR
train$fired <- ifelse(train$status == "fired", 1, 0)
train$status <- NULL

head(train)
```

```{r echo = FALSE, fig.align='center'}
knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
```

Prepare `HR_test` data and a `randomForest` model for the explainer:

```{r results="hide", eval = FALSE}
# fit a randomForest model
library("randomForest")
model <- randomForest(fired ~., data = train)

# prepare validation dataset
test <- DALEX::HR_test[1:1000,]
test$fired <- ifelse(test$status == "fired", 1, 0)
test$status <- NULL

# create an explainer for the model
explainer <- DALEX::explain(model,
                            data = test,
                            y = test$fired)

# start modelStudio
library("modelStudio")
```

-------------------------------------------------------------------

## modelStudio parameters

### instance explanations

Pass data points to the `new_observation` parameter for instance explanations
such as [Break Down](https://pbiecek.github.io/ema/breakDown.html),
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Ceteris Paribus](https://pbiecek.github.io/ema/ceterisParibus.html) Profiles.
Use `new_observation_y` to show their true labels.

```{r eval = FALSE}
new_observation <- test[1:3,]
rownames(new_observation) <- c("John Snow", "Arya Stark", "Samwell Tarly")
true_labels <- test[1:3,]$fired

modelStudio(explainer,
            new_observation = new_observation,
            new_observation_y  = true_labels)
```

### grid size

Achieve bigger or smaller `modelStudio` grid with `facet_dim` parameter.

```{r eval = FALSE}
# small dashboard with 2 panels
modelStudio(explainer,
            facet_dim = c(1,2))

# large dashboard with 9 panels
modelStudio(explainer,
            facet_dim = c(3,3))
```

### animations

Manipulate `time` parameter to set animation length. Value 0 will make
them invisible.

```{r eval = FALSE}
# slow down animations
modelStudio(explainer,
            time = 1000)

# turn off animations
modelStudio(explainer,
            time = 0)
```

### more calculations means more time

`N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles.
`B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
Decrease `N` and `B` parameters to lower the computation time or increase
them to get more accurate empirical results.

```{r eval = FALSE}
# faster, less precise
modelStudio(explainer,
            N = 200, B = 5)

# slower, more precise
modelStudio(explainer,
            N = 800, B = 25)
```

### no EDA mode

Don't compute the EDA plots if they are not needed. Set the `eda` parameter to `FALSE`.

```{r eval = FALSE}
modelStudio(explainer,
            eda = FALSE)
```

### progress bar

Hide computation progress bar messages with `show_info` parameter.

```{r eval = FALSE}
modelStudio(explainer,
            show_info = FALSE)
```

### viewer or browser?

Change `viewer` parameter to set where to display `modelStudio`.
Best described in `r2d3` documentation: [`r2d3 viewer argument`](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).

```{r eval = FALSE}
modelStudio(explainer,
            viewer = "browser")
```

-------------------------------------------------------------------

## parallel computation

Speed up `modelStudio` computation by setting `parallel` parameter to `TRUE`.
It uses [`parallelMap`](https://www.rdocumentation.org/packages/parallelMap) package
to calculate local explainers faster. It is really useful when using `modelStudio` with
complicated models, vast datasets or **many observations are being processed**.

All options can be set outside of function call.
More on that [here](https://github.com/berndbischl/parallelMap#being-lazy-configuration).

```{r eval = FALSE}
# set up the cluster
options(
  parallelMap.default.mode        = "socket",
  parallelMap.default.cpus        = 4,
  parallelMap.default.show.info   = FALSE
)

# calculations of local explanations will be distributed into 4 cores
modelStudio(explainer,
            new_observation = test[1:16,],
            parallel = TRUE)
```

--------------------------------------------------------------------

## plot options

Customize some of `modelStudio` looks by overwriting default options returned
by the `modelStudioOptions()` function. Full list of options:
[documentation](http://modelstudio.drwhy.ai/reference/modelStudioOptions.html).

```{r eval = FALSE}
# set additional graphical parameters
new_options <- modelStudioOptions(
  show_subtitle = TRUE,
  bd_subtitle = "Hello World",
  line_size = 5,
  point_size = 9,
  line_color = "pink",
  point_color = "purple",
  bd_positive_color = "yellow",
  bd_negative_color = "orange"
)

modelStudio(explainer,
            options = new_options)
```

-------------------------------------------------------------------

## DALEXtra

Use `explain_*()` functions from the [DALEXtra](https://github.com/ModelOriented/DALEXtra)
package to explain various models. Bellow basic example of making `modelStudio` for a `mlr` model using `explain_mlr()`.

```{r eval = FALSE}
library(DALEXtra)
library(mlr)

# fit a model
task <- makeRegrTask(id = "task", data = train, target = "fired")

learner <- makeLearner("regr.randomForest", par.vals = list(ntree = 300), predict.type = "response")

model <- train(learner, task)

# create an explainer for the model
explainer_mlr <- explain_mlr(model,
                             data = test,
                             y = test$fired,
                             label = "mlr")

# make a studio for the model
modelStudio(explainer_mlr,
            B = 10)
```

## References

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values plots are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

### 2020-04-13 R/modelStudio.R

@@ -1,14 +1,14 @@
-#' @title Generate Interactive Studio for Explanatory Model Analysis
+#' @title Interactive Studio for Explanatory Model Analysis
 #'
 #' @description
 #' This function computes various (instance and dataset level) model explanations and produces an interactive,
-#' customisable dashboard made with D3.js. It consists of multiple panels for plots with their short descriptions.
+#' customizable dashboard made with D3.js. It consists of multiple panels for plots with their short descriptions.
 #' Easily save and share the dashboard with others. Tools for model exploration unite with tools for EDA
 #' (Exploratory Data Analysis) to give a broad overview of the model behavior.
 #'
-#' Find more details about the plots in \href{https://github.com/pbiecek/ema}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
+#' Theoretical introduction to the plots: \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
 #'
-#' @param explainer An \code{explainer} created with function \code{DALEX::explain()}.
+#' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
 #' @param new_observation A new observation with columns that correspond to variables used in the model.
 #' @param new_observation_y True label for \code{new_observation} (optional).
 #' @param facet_dim Dimensions of the grid. Default is \code{c(2,2)}.
@@ -19,10 +19,10 @@
 #' @param eda Compute EDA plots. Default is \code{TRUE}.
 #' @param show_info Verbose progress on the console. Default is \code{TRUE}.
 #' @param parallel Speed up the computation using \code{parallelMap::parallelMap()}.
-#' See \href{https://modeloriented.github.io/modelStudio/articles/vignette_modelStudio.html#parallel-computation}{\bold{vignette}}.
+#' See \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html#parallel-computation}{\bold{vignette}}.
 #' This might interfere with showing progress using \code{show_info}.
 #' @param options Customize \code{modelStudio}. See \code{\link{modelStudioOptions}} and
-#' \href{https://modeloriented.github.io/modelStudio/articles/vignette_modelStudio.html#plot-options}{\bold{vignette}}.
[…]

### 2020-04-13 R/modelStudioOptions.R

@@ -45,27 +45,38 @@
 #' }
 #' }
 #'
+#' @references
+#'
+#' \itemize{
+#'   \item The input object is implemented in \href{https://modeloriented.github.io/DALEX/}{\bold{DALEX}}
+#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
+#' are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
+#'   \item Break Down and Shapley Values plots are implemented in \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
+#' }
+#'
+#' @seealso
+#' Vignettes: \href{https://modeloriented.github.io/modelStudio/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
+#' and \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
 #'
 #' @examples
 #' library("DALEX")
 #' library("modelStudio")
 #'
-#' # Create a model
-#' model_apartments <- glm(m2.price ~. ,
-#'                         data = apartments)
+#' # fit a model
+#' model_apartments <- glm(m2.price ~. , data = apartments)
 #'
-#' # Wrap it into an explainer
+#' # create an explainer for the model
 #' explainer_apartments <- DALEX::explain(model_apartments,
-#'                                        data = apartments[,-1],
-#'                                        y = apartments[,1],
-#'                                        verbose = FALSE)
+#'                                        data = apartments,
+#'                                        y = apartments$m2.price,
+#'                                        label = "glm")
 #'
-#' # Pick some data points
-#' new_apartments <- apartments[1:2,]
-#' rownames(new_apartments) <- c("ap1","ap2")
+#' # pick observations
+#' new_observation <- apartments[1:2,]
+#' rownames(new_observation) <- c("ap1","ap2")
 #'
-#' # Modify default options
-#' op <- modelStudioOptions(
+#' # modify default options
+#' new_options <- modelStudioOptions(
 #'   show_subtitle = TRUE,
 #'   bd_subtitle = "Hello World",
 #'   line_size = 5,
@@ -76,10 +87,11 @@
 #'   bd_negative_color = "orange"
 #' )
 #'
-#' # Make a studio for the model with modified option
-#' modelStudio(explainer_apartments, new_apartments,
-#'             N = 100, B = 10, options = op,
[…]

### 2020-04-13 inst/doc/ms-perks-features.R

@@ -1,0 +1,134 @@
+## ----setup, include = FALSE---------------------------------------------------
+knitr::opts_chunk$set(
+  collapse = FALSE,
+  comment = "#>",
+  warning = FALSE,
+  message = FALSE
+)
+
+## ----results="hide"-----------------------------------------------------------
+train <- DALEX::HR
+train$fired <- ifelse(train$status == "fired", 1, 0)
+train$status <- NULL
+
+head(train)
+
+## ----echo = FALSE, fig.align='center'-----------------------------------------
+knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
+
+## ----results="hide", eval = FALSE---------------------------------------------
+#  # fit a randomForest model
+#  library("randomForest")
+#  model <- randomForest(fired ~., data = train)
+#  
+#  # prepare validation dataset
+#  test <- DALEX::HR_test[1:1000,]
+#  test$fired <- ifelse(test$status == "fired", 1, 0)
+#  test$status <- NULL
+#  
+#  # create an explainer for the model
+#  explainer <- DALEX::explain(model,
+#                              data = test,
+#                              y = test$fired)
+#  
+#  # start modelStudio
+#  library("modelStudio")
+
+## ----eval = FALSE-------------------------------------------------------------
+#  new_observation <- test[1:3,]
+#  rownames(new_observation) <- c("John Snow", "Arya Stark", "Samwell Tarly")
+#  true_labels <- test[1:3,]$fired
+#  
+#  modelStudio(explainer,
+#              new_observation = new_observation,
+#              new_observation_y  = true_labels)
+
+## ----eval = FALSE-------------------------------------------------------------
+#  # small dashboard with 2 panels
+#  modelStudio(explainer,
+#              facet_dim = c(1,2))
+#  
+#  # large dashboard with 9 panels
+#  modelStudio(explainer,
+#              facet_dim = c(3,3))
+
+## ----eval = FALSE-------------------------------------------------------------
+#  # slow down animations
+#  modelStudio(explainer,
+#              time = 1000)
+#  
+#  # turn off animations
+#  modelStudio(explainer,
+#              time = 0)
+
+## ----eval = FALSE-------------------------------------------------------------
+#  # faster, less precise
+#  modelStudio(explainer,
+#              N = 200, B = 5)
+#  
+#  # slower, more precise
+#  modelStudio(explainer,
+#              N = 800, B = 25)
+
+## ----eval = FALSE-------------------------------------------------------------
[…]

### 2020-04-13 inst/doc/ms-r-python-examples.R

@@ -1,0 +1,253 @@
+## ----setup, include = FALSE---------------------------------------------------
+knitr::opts_chunk$set(
+  collapse = FALSE,
+  comment = "#>",
+  warning = FALSE,
+  message = FALSE,
+  eval = FALSE
+)
+
+## ----eval = FALSE-------------------------------------------------------------
+#  # packages for explainer objects
+#  install.packages("DALEX")
+#  install.packages("DALEXtra")
+#  
+#  # update main dependencies
+#  install.packages("ingredients")
+#  install.packages("iBreakDown")
+
+## ----eval = FALSE-------------------------------------------------------------
+#  # load packages and data
+#  library(mlr)
+#  library(DALEXtra)
+#  library(modelStudio)
+#  
+#  data <- DALEX::titanic_imputed
+#  
+#  # split the data
+#  index <- sample(1:nrow(data), 0.7*nrow(data))
+#  train <- data[index,]
+#  test <- data[-index,]
+#  
+#  # mlr ClassifTask takes target as factor
+#  train$survived <- as.factor(train$survived)
+#  
+#  # fit a model
+#  task <- makeClassifTask(id = "titanic", data = train, target = "survived")
+#  
+#  learner <- makeLearner("classif.ranger", predict.type = "prob")
+#  
+#  model <- train(learner, task)
+#  
+#  # create an explainer for the model
+#  explainer <- explain_mlr(model,
+#                           data = test,
+#                           y = test$survived,
+#                           label = "mlr")
+#  
+#  # pick observations
+#  new_observation <- test[1:2,]
+#  rownames(new_observation) <- c("id1", "id2")
+#  
+#  # make a studio for the model
+#  modelStudio(explainer,
+#              new_observation)
+
+## ----eval = FALSE-------------------------------------------------------------
+#  # load packages and data
+#  library(mlr3)
+#  library(mlr3learners)
+#  library(DALEXtra)
+#  library(modelStudio)
+#  
+#  data <- DALEX::titanic_imputed
+#  
+#  # split the data
+#  index <- sample(1:nrow(data), 0.7*nrow(data))
+#  train <- data[index,]
+#  test <- data[-index,]
+#  
+#  # mlr3 TaskClassif takes target as factor
+#  train$survived <- as.factor(train$survived)
+#  
+#  # fit a model
+#  task <- TaskClassif$new(id = "titanic", backend = train, target = "survived")
+#  
+#  learner <- lrn("classif.ranger", predict_type = "prob")
+#  
[…]

### 2020-04-13 inst/doc/vignette_modelStudio.R

@@ -1,150 +1,0 @@
-## ----setup, include = FALSE----------------------------------------------
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  warning = FALSE,
-  message = FALSE
-)
-
-## ----results="hide"------------------------------------------------------
-train <- DALEX::HR[1:100,]
-train$fired <- ifelse(train$status == "fired", 1, 0)
-train <- train[,-6]
-
-head(train)
-
-## ----echo = FALSE, fig.align='center'------------------------------------
-knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
-
-## ----results="hide", eval = FALSE----------------------------------------
-#  # create a random forest model
-#  library("randomForest")
-#  model <- randomForest(fired ~., data = train)
-#  
-#  # prepare validation dataset
-#  test <- DALEX::HR_test[1:100,]
-#  test$fired <- ifelse(test$status == "fired", 1, 0)
-#  test <- test[,-6]
-#  
-#  # create an explainer
-#  explainer <- DALEX::explain(model = model,
-#                              data = test[,-6],
-#                              y = test[,6],
-#                              verbose = FALSE)
-#  
-#  # start modelStudio
-#  library("modelStudio")
-
-## ----eval = FALSE--------------------------------------------------------
-#  new_observation <- test[1:3,]
-#  rownames(new_observation) <- c("John Snow", "Arya Stark", "Samwell Tarly")
-#  true_labels <- test[1:3,6]
-#  
-#  modelStudio(explainer, new_observation = new_observation,
-#                         new_observation_y  = true_labels)
-
-## ----eval = FALSE--------------------------------------------------------
-#  # small dashboard with 2 panels
-#  modelStudio(explainer, new_observation, facet_dim = c(1,2))
-#  
-#  # large dashboard with 9 panels
-#  modelStudio(explainer, new_observation, facet_dim = c(3,3))
-
-## ----eval = FALSE--------------------------------------------------------
-#  # slow down animations
-#  modelStudio(explainer, new_observation, time = 1000)
-#  
-#  # turn off animations
-#  modelStudio(explainer, new_observation, time = 0)
-
-## ----eval = FALSE--------------------------------------------------------
-#  modelStudio(explainer, new_observation, N = 100, B = 10)
-#  
-#  modelStudio(explainer, new_observation, N = 1000, B = 50)
-
[…]

### 2020-05-08 inst/doc/ms-perks-features.Rmd
version 1.1.0

@@
 
-`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces an interactive, customizable dashboard made with D3.js.
-It consists of multiple panels for plots with their short descriptions.
-Easily save and share the dashboard with others.
-Tools for model exploration unite with tools for EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.
+`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces
+an interactive, customisable dashboard. It consists of multiple panels for plots with their short descriptions.
+Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for
+EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.
 
@@
 train <- DALEX::HR
-train$fired <- ifelse(train$status == "fired", 1, 0)
+train$fired <- as.factor(ifelse(train$status == "fired", 1, 0))
 train$status <- NULL
@@
 
-Prepare `HR_test` data and a `randomForest` model for the explainer:
+Prepare `HR_test` data and a `ranger` model for the explainer:
 
 ```{r results="hide", eval = FALSE}
-# fit a randomForest model
-library("randomForest")
-model <- randomForest(fired ~., data = train)
+# fit a ranger model
+library("ranger")
+model <- ranger(fired ~., data = train, probability = TRUE)
 
@@
 and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
+`10*N` is a number of observations used for calculation of
+[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
 `B` is a number of permutation rounds used for calculation of
@@
 modelStudio(explainer,
-            N = 800, B = 25)
+            N = 500, B = 15)
 ```
@@
 Change `viewer` parameter to set where to display `modelStudio`.
-Best described in `r2d3` documentation: [`r2d3 viewer argument`](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).
+Best described in `r2d3` documentation:
+[`r2d3 viewer argument`](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).
 
@@
 
-## plot options
+## additional options
 
 Customize some of `modelStudio` looks by overwriting default options returned
-by the `modelStudioOptions()` function. Full list of options:
-[documentation](http://modelstudio.drwhy.ai/reference/modelStudioOptions.html).
+by the `ms_options()` function. Full list of options:
+[documentation](http://modelstudio.drwhy.ai/reference/ms_options.html).
 
@@
 # set additional graphical parameters
-new_options <- modelStudioOptions(
+new_options <- ms_options(
   show_subtitle = TRUE,
@@
 
+All visual options can be changed after the calculations using `ms_update_options()`.
+
+```{r eval = FALSE}
+old_ms <- modelStudio(explainer)
+old_ms
+
+# update the options
+new_ms <- ms_update_options(old_ms,
+                            time = 0,
+                            facet_dim = c(1,2),
+                            margin_left = 150)
+new_ms
+```
+
 -------------------------------------------------------------------
+
+## update observations
+
+Use `ms_update_observations()` to add more observations with their local explanations to the `modelStudio`.
+
+```{r eval = FALSE}
+old_ms <- modelStudio(explainer)
+old_ms
+
+# add new observations
+plus_ms <- ms_update_observations(old_ms,
+                                  explainer,
+                                  new_observation = test[101:102,])
+plus_ms
+
+# overwrite old observations
+new_ms <- ms_update_observations(old_ms,
+                                 explainer,
+                                 new_observation = test[103:104,],
+                                 overwrite = TRUE)
+new_ms
+```
 
@@
 Use `explain_*()` functions from the [DALEXtra](https://github.com/ModelOriented/DALEXtra)
-package to explain various models. Bellow basic example of making `modelStudio` for a `mlr` model using `explain_mlr()`.
+package to explain various models. Bellow basic example of making `modelStudio` for
+a `mlr` model using `explain_mlr()`.
 
@@
 # fit a model
-task <- makeRegrTask(id = "task", data = train, target = "fired")
-
-learner <- makeLearner("regr.randomForest", par.vals = list(ntree = 300), predict.type = "response")
-
+task <- makeClassifTask(id = "task", data = train, target = "fired")
+learner <- makeLearner("classif.ranger", predict.type = "prob")
 model <- train(learner, task)
@@
 # make a studio for the model
-modelStudio(explainer_mlr,
-            B = 10)
+modelStudio(explainer_mlr)
 ```

### 2020-05-08 inst/doc/ms-r-python-examples.Rmd
version 1.1.0

---
title: "modelStudio - R & Python examples"
author: "Hubert Baniecki"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{modelStudio - R & Python examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  eval = FALSE
)
```

# R & Python Examples

## R

The `modelStudio()` function uses `DALEX` explainers created with `DALEX::explain()` or `DALEXtra::explain_*()`.

```{r eval = FALSE}
# packages for explainer objects
install.packages("DALEX")
install.packages("DALEXtra")

# update main dependencies
install.packages("ingredients")
install.packages("iBreakDown")
```

### mlr [dashboard](https://modeloriented.github.io/modelStudio/mlr.html)

In this example we will make a studio for the `ranger` model on `apartments` data.

```{r eval = FALSE}
# load packages and data
library(mlr)
library(DALEXtra)
library(modelStudio)

data <- DALEX::apartments

# split the data
index <- sample(1:nrow(data), 0.7*nrow(data))
train <- data[index,]
test <- data[-index,]

# fit a model
task <- makeRegrTask(id = "apartments", data = train, target = "m2.price")
learner <- makeLearner("regr.ranger", predict.type = "response")
model <- train(learner, task)

# create an explainer for the model
explainer <- explain_mlr(model,
                         data = test,
                         y = test$m2.price,
                         label = "mlr")

# pick observations
new_observation <- test[1:2,]
rownames(new_observation) <- c("id1", "id2")

# make a studio for the model
modelStudio(explainer,
            new_observation)
```

### mlr3 [dashboard](https://modeloriented.github.io/modelStudio/mlr3.html)

In this example we will make a studio for the `ranger` model on `titanic` data.

```{r eval = FALSE}
# load packages and data
library(mlr3)
library(mlr3learners)
library(DALEXtra)
library(modelStudio)

data <- DALEX::titanic_imputed

# split the data
index <- sample(1:nrow(data), 0.7*nrow(data))
train <- data[index,]
test <- data[-index,]

# mlr3 TaskClassif takes target as factor
train$survived <- as.factor(train$survived)

# fit a model
task <- TaskClassif$new(id = "titanic", backend = train, target = "survived")
learner <- lrn("classif.ranger", predict_type = "prob")
learner$train(task)

# create an explainer for the model
explainer <- explain_mlr3(learner,
                          data = test,
                          y = test$survived,
                          label = "mlr3")

# pick observations
new_observation <- test[1:2,]
rownames(new_observation) <- c("id1", "id2")

# make a studio for the model
modelStudio(explainer,
            new_observation)
```

### xgboost [dashboard](https://modeloriented.github.io/modelStudio/xgboost.html)

In this example we will make a studio for the `xgboost` model on `titanic` data.

```{r eval = FALSE}
# load packages and data
library(xgboost)
library(DALEX)
library(modelStudio)

data <- DALEX::titanic_imputed

# split the data
index <- sample(1:nrow(data), 0.7*nrow(data))
train <- data[index,]
test <- data[-index,]

train_matrix <- model.matrix(survived ~.-1, train)
test_matrix <- model.matrix(survived ~.-1, test)

# fit a model
xgb_matrix <- xgb.DMatrix(train_matrix, label = train$survived)
params <- list(max_depth = 3, objective = "binary:logistic", eval_metric = "auc")
model <- xgb.train(params, xgb_matrix, nrounds = 500)

# create an explainer for the model
explainer <- explain(model,
                     data = test_matrix,
                     y = test$survived,
                     label = "xgboost")

# pick observations
new_observation <- test_matrix[1:2, , drop=FALSE]
rownames(new_observation) <- c("id1", "id2")

# make a studio for the model
modelStudio(explainer,
            new_observation,
            options = ms_options(margin_left = 140))
```

### caret [dashboard](https://modeloriented.github.io/modelStudio/caret.html)

In this example we will make a studio for the `gbm` model on `titanic` data.

```{r eval = FALSE}
# load packages and data
library(caret)
library(DALEX)
library(modelStudio)

data <- DALEX::titanic_imputed

# split the data
index <- sample(1:nrow(data), 0.7*nrow(data))
train <- data[index,]
test <- data[-index,]

# caret train takes target as factor
train$survived <- as.factor(train$survived)

# fit a model
cv <- trainControl(method = "repeatedcv", number = 3, repeats = 3)
model <- train(survived ~ ., data = train, method = "gbm", trControl = cv, verbose = FALSE)

# create an explainer for the model
explainer <- explain(model,
                     data = test,
                     y = test$survived,
                     label = "caret")

# pick observations
new_observation <- test[1:2,]
rownames(new_observation) <- c("id1", "id2")

# make a studio for the model
modelStudio(explainer,
            new_observation)
```

### h2o [dashboard](https://modeloriented.github.io/modelStudio/h2o.html)

In this example we will make a studio for the `h2o.automl` model on `titanic` data.

```{r eval = FALSE}
# load packages and data
library(h2o)
library(DALEXtra)
library(modelStudio)

data <- DALEX::titanic_imputed

# init h2o
h2o.init()
h2o.no_progress()

# split the data
h2o_split <- h2o.splitFrame(as.h2o(data))
train <- h2o_split[[1]]
test <- as.data.frame(h2o_split[[2]])

# h2o automl takes target as factor
train$survived <- as.factor(train$survived)

# fit a model
automl <- h2o.automl(y = "survived", training_frame = train, max_runtime_secs = 30)
model <- automl@leader

# create an explainer for the model
explainer <- explain_h2o(model,
                         data = test,
                         y = test$survived,
                         label = "h2o")

# pick observations
new_observation <- test[1:2,]
rownames(new_observation) <- c("id1", "id2")

# make a studio for the model
modelStudio(explainer,
            new_observation,
            B = 5)

# shutdown h2o
h2o.shutdown(prompt = FALSE)
```

### parsnip [dashboard](https://modeloriented.github.io/modelStudio/parsnip.html)

In this example we will make a studio for the `ranger` model on `apartments` data.

```{r eval=FALSE}
# load packages and data
library(parsnip)
library(DALEX)
library(modelStudio)

data <- DALEX::apartments

# split the data
index <- sample(1:nrow(data), 0.7*nrow(data))
train <- data[index,]
test <- data[-index,]

# fit a model
model <- rand_forest() %>%
  set_engine("ranger", importance = "impurity") %>%
  set_mode("regression") %>%
  fit(m2.price ~ ., data = train)

# create an explainer for the model
explainer <- explain(model,
                     data = test,
                     y = test$m2.price,
                     label = "parsnip")

# make a studio for the model
modelStudio(explainer)
```

## Python

The `modelStudio()` function uses `dalex` explainers created with `dalex.Explainer()`.

```{bash, eval=FALSE, engine="sh"}
# package for Explainer object
pip3 install dalex --force
```

Use `pickle` Python module and `reticulate` R package to easily make a studio for a model.

```{r eval = FALSE}
# package for pickle load
install.packages("reticulate")

# update main dependencies
install.packages("ingredients")
install.packages("iBreakDown")
```

### scikit-learn [dashboard](https://modeloriented.github.io/modelStudio/scikitlearn.html)

In this example we will make a studio for the `Pipeline SVR` model on `fifa` data.

First, use `dalex` in Python:

```{python, python.reticulate = FALSE, eval = FALSE}
# load packages and data
import dalex as dx
from sklearn.model_selection import train_test_split
from sklearn.pipeline import Pipeline
from sklearn.preprocessing import StandardScaler
from sklearn.svm import SVR
from numpy import log

data = dx.datasets.load_fifa()
X = data.drop(columns=['overall', 'potential', 'value_eur', 'wage_eur', 'nationality'], axis=1)
y = log(data.value_eur)

# split the data
X_train, X_test, y_train, y_test = train_test_split(X, y)

# fit a pipeline model
model = Pipeline([('scale', StandardScaler()), ('svm', SVR())])
model.fit(X_train, y_train)

# create an explainer for the model
explainer = dx.Explainer(model, data=X_test, y=y_test, label='scikit-learn')

# pack the explainer into a pickle file
explainer.dump(open('explainer_scikitlearn.pickle', 'wb'))
```

Then, use `modelStudio` in R:

```{r eval = FALSE}
# load the explainer from the pickle file
library(reticulate)
explainer <- py_load_object("explainer_scikitlearn.pickle", pickle = "pickle")

# make a studio for the model
library(modelStudio)
modelStudio(explainer, B = 5,
            options = ms_options(margin_left = 160))
```

### lightGBM [dashboard](https://modeloriented.github.io/modelStudio/lightgbm.html)

In this example we will make a studio for the `Pipeline LGBMClassifier` model on `titanic` data.

First, use `dalex` in Python:

```{python, python.reticulate = FALSE, eval = FALSE}
# load packages and data
import dalex as dx
from sklearn.model_selection import train_test_split
from sklearn.pipeline import Pipeline
from sklearn.preprocessing import StandardScaler, OneHotEncoder
from sklearn.impute import SimpleImputer
from sklearn.compose import ColumnTransformer
from lightgbm import LGBMClassifier

data = dx.datasets.load_titanic()
X = data.drop(columns='survived')
y = data.survived

# split the data
X_train, X_test, y_train, y_test = train_test_split(X, y)

# fit a pipeline model
numerical_features = ['age', 'fare', 'sibsp', 'parch']
numerical_transformer = Pipeline(
  steps=[
    ('imputer', SimpleImputer(strategy='median')),
    ('scaler', StandardScaler())
  ]
)
categorical_features = ['gender', 'class', 'embarked']
categorical_transformer = Pipeline(
  steps=[
    ('imputer', SimpleImputer(strategy='constant', fill_value='missing')),
    ('onehot', OneHotEncoder(handle_unknown='ignore'))
  ]
)

preprocessor = ColumnTransformer(
  transformers=[
    ('num', numerical_transformer, numerical_features),
    ('cat', categorical_transformer, categorical_features)
  ]
)

classifier = LGBMClassifier(n_estimators=300)

model = Pipeline(
  steps=[
    ('preprocessor', preprocessor),
    ('classifier', classifier)
  ]
)
model.fit(X_train, y_train)

# create an explainer for the model
explainer = dx.Explainer(model, data=X_test, y=y_test, label='lightGBM')

# pack the explainer into a pickle file
explainer.dump(open('explainer_lightgbm.pickle', 'wb')) 
```

Then, use `modelStudio` in R:

```{r eval = FALSE}
# load the explainer from the pickle file
library(reticulate)
explainer <- py_load_object("explainer_lightgbm.pickle", pickle = "pickle")

# make a studio for the model
library(modelStudio)
modelStudio(explainer)
```

### keras/tensorflow [dashboard](https://modeloriented.github.io/modelStudio/keras.html)

In this example we will make a studio for the `Pipeline KerasClassifier` model on `titanic` data.

First, use `dalex` in Python:

```{python, python.reticulate = FALSE, eval = FALSE}
# load packages and data
import dalex as dx
from sklearn.model_selection import train_test_split
from sklearn.pipeline import Pipeline
from sklearn.preprocessing import StandardScaler, OneHotEncoder
from sklearn.impute import SimpleImputer
from sklearn.compose import ColumnTransformer
from keras.wrappers.scikit_learn import KerasClassifier
from keras.layers import Dense
from keras.models import Sequential

data = dx.datasets.load_titanic()
X = data.drop(columns='survived')
y = data.survived

# split the data
X_train, X_test, y_train, y_test = train_test_split(X, y)

# fit a pipeline model
numerical_features = ['age', 'fare', 'sibsp', 'parch']
numerical_transformer = Pipeline(
  steps=[
    ('imputer', SimpleImputer(strategy='median')),
    ('scaler', StandardScaler())
  ]
)
categorical_features = ['gender', 'class', 'embarked']
categorical_transformer = Pipeline(
  steps=[
    ('imputer', SimpleImputer(strategy='constant', fill_value='missing')),
    ('onehot', OneHotEncoder(handle_unknown='ignore'))
  ]
)

preprocessor = ColumnTransformer(
  transformers=[
    ('num', numerical_transformer, numerical_features),
    ('cat', categorical_transformer, categorical_features)
  ]
)

def create_architecture():
    model = Sequential()
    # there are 17 inputs after the pipeline
    model.add(Dense(60, input_dim=17, activation='relu'))
    model.add(Dense(1, activation='sigmoid'))
    model.compile(loss='binary_crossentropy', optimizer='adam', metrics=['accuracy'])
    return model

classifier = KerasClassifier(build_fn=create_architecture,
                             epochs=100, batch_size=32, verbose=False)

model = Pipeline(
  steps=[
    ('preprocessor', preprocessor),
    ('classifier', classifier)
  ]
)
model.fit(X_train, y_train)

# create an explainer for the model
explainer = dx.Explainer(model, data=X_test, y=y_test, label='keras')

# pack the explainer into a pickle file
explainer.dump(open('explainer_keras.pickle', 'wb'))
```

Then, use `modelStudio` in R:

```{r eval = FALSE}
# load the explainer from the pickle file
library(reticulate)

#! add blank create_architecture function before load !
py_run_string("
def create_architecture():
    return True
")

explainer <- py_load_object("explainer_keras.pickle", pickle = "pickle")

# make a studio for the model
library(modelStudio)
modelStudio(explainer)
```

## References

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values plots are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

### 2020-05-08 R/modelStudio.R

@@ -2,35 +2,42 @@
 #'
 #' @description
 #' This function computes various (instance and dataset level) model explanations and produces an interactive,
-#' customizable dashboard made with D3.js. It consists of multiple panels for plots with their short descriptions.
-#' Easily save and share the dashboard with others. Tools for model exploration unite with tools for EDA
+#' customisable dashboard. It consists of multiple panels for plots with their short descriptions.
+#' Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for EDA
 #' (Exploratory Data Analysis) to give a broad overview of the model behavior.
 #'
-#' Theoretical introduction to the plots: \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
+#' Theoretical introduction to the plots:
+#' \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
 #'
 #' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
-#' @param new_observation A new observation with columns that correspond to variables used in the model.
+#' @param new_observation New observations with columns that correspond to variables used in the model.
 #' @param new_observation_y True label for \code{new_observation} (optional).
 #' @param facet_dim Dimensions of the grid. Default is \code{c(2,2)}.
-#' @param time Time in ms. Set animation length. Default is \code{500}.
-#' @param max_features Maximum number of features to be included in Break Down and Shapley Values plots. Default is \code{10}.
-#' @param N Number of observations used for calculation of partial dependence profiles. Default is \code{400}.
-#' @param B Number of random paths used for calculation of Shapley values. Default is \code{15}.
+#' @param time Time in ms. Set the animation length. Default is \code{500}.
+#' @param max_features Maximum number of features to be included in BD and SV plots.
+#'  Default is \code{10}.
+#' @param N Number of observations used for the calculation of PD and AD.
+#'  \code{10*N} is a number of observations used for the calculation of FI.
+#'  Default \code{N} is \code{300}.
[…]

### 2020-05-08 R/ms_options.R

@@ -6,10 +6,11 @@
 #' parameter in the main function. \strong{WARNING: Editing default options may cause
 #' unintended behavior.}
 #'
-#' @param ... Options to change, \code{option_name = value}.
+#' @param ... Options to change in the form \code{option_name = value}.
 #'
 #' @return \code{list} of options for \code{modelStudio}.
 #'
+#' @section Options:
 #' \subsection{Main options:}{
 #' \describe{
 #' \item{scale_plot}{\code{TRUE} Makes every plot the same height, ignores \code{bar_width}.}
@@ -66,17 +67,16 @@
 #' model_apartments <- glm(m2.price ~. , data = apartments)
 #'
 #' # create an explainer for the model
-#' explainer_apartments <- DALEX::explain(model_apartments,
-#'                                        data = apartments,
-#'                                        y = apartments$m2.price,
-#'                                        label = "glm")
+#' explainer_apartments <- explain(model_apartments,
+#'                                 data = apartments,
+#'                                 y = apartments$m2.price)
 #'
 #' # pick observations
 #' new_observation <- apartments[1:2,]
 #' rownames(new_observation) <- c("ap1","ap2")
 #'
 #' # modify default options
-#' new_options <- modelStudioOptions(
+#' new_options <- ms_options(
 #'   show_subtitle = TRUE,
 #'   bd_subtitle = "Hello World",
 #'   line_size = 5,
@@ -91,11 +91,11 @@
 #' modelStudio(explainer_apartments,
 #'             new_observation,
 #'             options = new_options,
-#'             N = 100,  B = 10) # faster example
+#'             N = 200,  B = 5) # faster example
 #'
 #' @export
-#' @rdname modelStudioOptions
-modelStudioOptions <- function(...) {
+#' @rdname ms_options
+ms_options <- function(...) {
 
   # prepare default options
   default_options <- list(
@@ -177,8 +177,17 @@ modelStudioOptions <- function(...) {
     at_point_color = "#371ea3"
   )
 
-  # input user options
+  # input new options
   default_options[names(list(...))] <- list(...)
 
   default_options
+}
+
+#' deprecated since v1.1
+#' @export
+#' @rdname ms_options
+modelStudioOptions <- function(...) {
+  warning("The 'modelStudioOptions()' function is deprecated; please use 'ms_options()' instead.")
+  ret <- ms_options(...)
+  ret
 }

### 2020-05-08 R/ms_update_observations.R

@@ -1,0 +1,278 @@
+#' @title Update the observations of a modelStudio object
+#'
+#' @description
+#' This function calculates local explanations on new observations and adds them
+#' to a \code{modelStudio} object.
+#'
+#' @param object A \code{modelStudio} created with \code{modelStudio()}.
+#' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
+#' @param new_observation New observations with columns that correspond to variables used in the model.
+#' @param new_observation_y True label for \code{new_observation} (optional).
+#' @param max_features Maximum number of features to be included in BD and SV plots.
+#'  Default is \code{10}.
+#' @param B Number of permutation rounds used for calculation of SV and FI.
+#'  Default is \code{10}.
+#'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#more-calculations-means-more-time}{\bold{vignette}}
+#' @param show_info Verbose a progress on the console. Default is \code{TRUE}.
+#' @param parallel Speed up the computation using \code{parallelMap::parallelMap()}.
+#'  See \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html#parallel-computation}{\bold{vignette}}.
+#'  This might interfere with showing progress using \code{show_info}.
+#' @param overwrite Overwrite existing observations and their explanations.
+#'  Default is \code{FALSE} which means add new observations to the existing ones.
+#' @param ... Other parameters.
+#'
+#' @return An object of the \code{r2d3, htmlwidget, modelStudio} class.
+#'
+#' @references
+#'
+#' \itemize{
+#'   \item The input object is implemented in \href{https://modeloriented.github.io/DALEX/}{\bold{DALEX}}
+#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
+#' are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
+#'   \item Break Down and Shapley Values plots are implemented in \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
+#' }
+#'
+#' @seealso
+#' Vignettes: \href{https://modeloriented.github.io/modelStudio/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
+#' and \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
+#'
+#' @examples
+#' library("DALEX")
+#' library("modelStudio")
+#'
[…]

### 2020-05-08 R/ms_update_options.R

@@ -1,0 +1,95 @@
+#' @title Update the options of a modelStudio object
+#'
+#' @description
+#' This function updates the options of a \code{\link{modelStudio}} object.
+#' \strong{WARNING: Editing default options may cause unintended behavior.}
+#'
+#' @param object A \code{modelStudio} created with \code{modelStudio()}.
+#' @param ... Options to change in the form \code{option_name = value},
+#'  e.g. \code{time = 0}, \code{facet_dim = c(1,2)}.
+#'
+#' @return An object of the \code{r2d3, htmlwidget, modelStudio} class.
+#'
+#' @inheritSection ms_options Options
+#'
+#' @references
+#'
+#' \itemize{
+#'   \item The input object is implemented in \href{https://modeloriented.github.io/DALEX/}{\bold{DALEX}}
+#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
+#' are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
+#'   \item Break Down and Shapley Values plots are implemented in \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
+#' }
+#'
+#' @seealso
+#' Vignettes: \href{https://modeloriented.github.io/modelStudio/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
+#' and \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
+#'
+#' @examples
+#' library("DALEX")
+#' library("modelStudio")
+#'
+#' # fit a model
+#' model_titanic <- glm(survived ~., data = titanic_imputed, family = "binomial")
+#'
+#' # create an explainer for the model
+#' explainer_titanic <- explain(model_titanic,
+#'                              data = titanic_imputed,
+#'                              y = titanic_imputed$survived)
+#'
+#' # make a studio for the model
+#' ms <- modelStudio(explainer_titanic)
+#'
+#' # update the options
+#' new_ms <- ms_update_options(ms,
+#'                             time = 0,
+#'                             facet_dim = c(1,2),
+#'                             margin_left = 150)
+#' new_ms
+#'
+#' @export
+#' @rdname ms_update_options
+ms_update_options <- function(object, ...) {
+
+  stopifnot("modelStudio" %in% class(object))
+
+  # extract old options
+  old_options <- object$x$options
[…]

### 2020-05-08 inst/doc/ms-perks-features.R

@@ -8,7 +8,7 @@ knitr::opts_chunk$set(
 
 ## ----results="hide"-----------------------------------------------------------
 train <- DALEX::HR
-train$fired <- ifelse(train$status == "fired", 1, 0)
+train$fired <- as.factor(ifelse(train$status == "fired", 1, 0))
 train$status <- NULL
 
 head(train)
@@ -17,9 +17,9 @@ head(train)
 knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 
 ## ----results="hide", eval = FALSE---------------------------------------------
-#  # fit a randomForest model
-#  library("randomForest")
-#  model <- randomForest(fired ~., data = train)
+#  # fit a ranger model
+#  library("ranger")
+#  model <- ranger(fired ~., data = train, probability = TRUE)
 #  
 #  # prepare validation dataset
 #  test <- DALEX::HR_test[1:1000,]
@@ -68,7 +68,7 @@ knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 #  
 #  # slower, more precise
 #  modelStudio(explainer,
-#              N = 800, B = 25)
+#              N = 500, B = 15)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  modelStudio(explainer,
@@ -97,7 +97,7 @@ knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # set additional graphical parameters
-#  new_options <- modelStudioOptions(
+#  new_options <- ms_options(
 #    show_subtitle = TRUE,
 #    bd_subtitle = "Hello World",
 #    line_size = 5,
@@ -112,14 +112,40 @@ knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 #              options = new_options)
 
 ## ----eval = FALSE-------------------------------------------------------------
+#  old_ms <- modelStudio(explainer)
+#  old_ms
+#  
+#  # update the options
+#  new_ms <- ms_update_options(old_ms,
+#                              time = 0,
+#                              facet_dim = c(1,2),
+#                              margin_left = 150)
+#  new_ms
+
+## ----eval = FALSE-------------------------------------------------------------
+#  old_ms <- modelStudio(explainer)
+#  old_ms
+#  
+#  # add new observations
+#  plus_ms <- ms_update_observations(old_ms,
+#                                    explainer,
[…]

### 2020-05-08 inst/doc/ms-r-python-examples.R

@@ -22,27 +22,22 @@ knitr::opts_chunk$set(
 #  library(DALEXtra)
 #  library(modelStudio)
 #  
-#  data <- DALEX::titanic_imputed
+#  data <- DALEX::apartments
 #  
 #  # split the data
 #  index <- sample(1:nrow(data), 0.7*nrow(data))
 #  train <- data[index,]
 #  test <- data[-index,]
 #  
-#  # mlr ClassifTask takes target as factor
-#  train$survived <- as.factor(train$survived)
-#  
 #  # fit a model
-#  task <- makeClassifTask(id = "titanic", data = train, target = "survived")
-#  
-#  learner <- makeLearner("classif.ranger", predict.type = "prob")
-#  
+#  task <- makeRegrTask(id = "apartments", data = train, target = "m2.price")
+#  learner <- makeLearner("regr.ranger", predict.type = "response")
 #  model <- train(learner, task)
 #  
 #  # create an explainer for the model
 #  explainer <- explain_mlr(model,
 #                           data = test,
-#                           y = test$survived,
+#                           y = test$m2.price,
 #                           label = "mlr")
 #  
 #  # pick observations
@@ -72,9 +67,7 @@ knitr::opts_chunk$set(
 #  
 #  # fit a model
 #  task <- TaskClassif$new(id = "titanic", backend = train, target = "survived")
-#  
 #  learner <- lrn("classif.ranger", predict_type = "prob")
-#  
 #  learner$train(task)
 #  
 #  # create an explainer for the model
@@ -109,9 +102,7 @@ knitr::opts_chunk$set(
 #  
 #  # fit a model
 #  xgb_matrix <- xgb.DMatrix(train_matrix, label = train$survived)
-#  
-#  params <- list(max_depth = 7, objective = "binary:logistic", eval_metric = "auc")
-#  
+#  params <- list(max_depth = 3, objective = "binary:logistic", eval_metric = "auc")
 #  model <- xgb.train(params, xgb_matrix, nrounds = 500)
 #  
 #  # create an explainer for the model
@@ -127,7 +118,7 @@ knitr::opts_chunk$set(
 #  # make a studio for the model
 #  modelStudio(explainer,
 #              new_observation,
-#              options = modelStudioOptions(margin_left = 140))
+#              options = ms_options(margin_left = 140))
 
 ## ----eval = FALSE-------------------------------------------------------------
[…]

### 2020-05-08 tests/testthat/test_ms_update_observations.R

@@ -1,0 +1,31 @@
+context("Check ms_update_observations() function")
+
+source("test_objects.R")
+
+ms <- modelStudio::modelStudio(explain_rf, apartments[1:2,], N = 5, B = 2, show_info = v)
+
+testthat::test_that("modelStudio class", {
+  testthat::expect_is(ms, "modelStudio")
+  testthat::expect_silent(ms)
+})
+
+new_ms1 <- modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v)
+new_ms2 <- modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v,
+                                               new_observation = apartments[100:101,],
+                                               overwrite = FALSE)
+new_ms3 <- modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v,
+                                               new_observation = apartments[1:2,],
+                                               overwrite = TRUE)
+
+testthat::test_that("ms_update_observations", {
+  testthat::expect_is(new_ms1, "modelStudio")
+  testthat::expect_silent(modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v))
+  testthat::expect_is(new_ms2, "modelStudio")
+  testthat::expect_silent(modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v,
+                                                              new_observation = apartments[100:101,],
+                                                              overwrite = FALSE))
+  testthat::expect_is(new_ms3, "modelStudio")
+  testthat::expect_silent(modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v,
+                                                              new_observation = apartments[1:2,],
+                                                              overwrite = TRUE))
+})

### 2020-05-08 tests/testthat/test_ms_update_options.R

@@ -1,0 +1,27 @@
+context("Check ms_update_options() function")
+
+source("test_objects.R")
+
+ms <- modelStudio::modelStudio(explain_rf, apartments[1:2,],
+                               facet_dim = c(2,3), N = 5, B = 2, show_info = v)
+
+testthat::test_that("modelStudio class", {
+  testthat::expect_is(ms, "modelStudio")
+  testthat::expect_silent(modelStudio::modelStudio(explain_rf, apartments[1:2,],
+                                                   facet_dim = c(2,3), N = 5, B = 2, show_info = v))
+})
+
+new_ms <- modelStudio::ms_update_options(ms, facet_dim = c(1,2), time = 0,
+                                         margin_left = 100)
+
+testthat::test_that("ms_update_options", {
+  testthat::expect_is(new_ms, "modelStudio")
+  testthat::expect_equal(new_ms$x$options$time, 0)
+  testthat::expect_equal(new_ms$x$options$margin_left, 100)
+  testthat::expect_equal(new_ms$x$options$facet_dim, c(1,2))
+})
+
+testthat::test_that("ms_update_options run", {
+  testthat::expect_silent(modelStudio::ms_update_options(ms, facet_dim = c(1,2), time = 0,
+                                                         margin_left = 100, show_info = v))
+})

### 2020-05-08 tests/testthat/test_warnings_and_errors.R

@@ -1,4 +1,4 @@
-context("Check modelStudio() function for warnings and errors")
+context("Check functions for warnings and errors")
 
 source("test_objects.R")
 
@@ -6,7 +6,7 @@ testthat::test_that("new_observation as list", {
   testthat::expect_warning(
     modelStudio::modelStudio(explain_glm,
                              new_observation = as.list(titanic_test[1,-9]),
-                             show_info = v)
+                             show_info = v, B = 3)
   )
 })
 
@@ -14,7 +14,26 @@ testthat::test_that("check_single_prediction error", {
   testthat::expect_error(
     modelStudio::modelStudio(explainer_xgb,
                              new_observation = model_matrix_train[1,],
-                             show_info = v)
+                             show_info = v, B = 3)
   )
 })
 
+testthat::test_that("deprecated modelStudioOptions", {
+  testthat::expect_warning(
+    modelStudio::modelStudioOptions()
+  )
+})
+
+ms <- modelStudio::modelStudio(explain_rf, apartments[1:2,], N = 5, B = 2, show_info = v)
+new_ms <- modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v,
+                                              new_observation = apartments[1,],
+                                              new_observation_y = apartments$m2.price[1])
+
+testthat::test_that("duplicated ids", {
+  testthat::expect_is(new_ms, "modelStudio")
+  testthat::expect_warning(
+    modelStudio::ms_update_observations(ms, explain_rf, B = 2, show_info = v,
+                                       new_observation = apartments[1,],
+                                       new_observation_y = apartments$m2.price[1])
+  )
+})

### 2020-07-15 R/modelStudio.R
version 1.2.0

@@ -3,11 +3,14 @@
 #' @description
 #' This function computes various (instance and dataset level) model explanations and produces an interactive,
 #' customisable dashboard. It consists of multiple panels for plots with their short descriptions.
-#' Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for EDA
-#' (Exploratory Data Analysis) to give a broad overview of the model behavior.
+#' Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for
+#' Exploratory Data Analysis to give a broad overview of the model behavior.
 #'
 #' Theoretical introduction to the plots:
 #' \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
+#'
+#' Displayed variable can be changed by clicking on the bars of plots or with the first dropdown list,
+#'  and observation can be changed with the second dropdown list.
 #'
 #' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
 #' @param new_observation New observations with columns that correspond to variables used in the model.
@@ -176,15 +179,15 @@ modelStudio.explainer <- function(explainer,
 
   } else if (is.null(dim(new_observation))) {
     warning("`new_observation` argument is not a data.frame nor a matrix, coerced to data.frame\n")
-    new_observation <- as.data.frame(new_observation)
+    new_observation <- as.data.frame(new_observation, stringsAsFactors=TRUE)
 
   } else if (is.null(rownames(new_observation))) {
     rownames(new_observation) <- 1:nrow(new_observation)
   }
 
   check_single_prediction <- try(predict_function(model, new_observation[1,, drop = FALSE]), silent = TRUE)
-  if (class(check_single_prediction)[1] == "try-error") {
-    stop("`predict_function` returns an error when executed on `new_observation[1,, drop = FALSE]` \n")
+  if ("try-error" %in% class(check_single_prediction)) {
+    stop("`explainer$predict_function` returns an error when executed on `new_observation[1,, drop = FALSE]` \n")
   }
   #:#
 
@@ -345,7 +348,8 @@ modelStudio.explainer <- function(explainer,
   between <- " - "
   if (is.null(new_observation_y)) new_observation_y <- between <- ""
   drop_down_data <- as.data.frame(cbind(rownames(obs_data),
-                                        paste0(rownames(obs_data), between, new_observation_y)))
+                                        paste0(rownames(obs_data), between, new_observation_y)),
[…]

### 2020-07-15 inst/d3js/generatePlots.js

@@ -246,6 +246,7 @@ function breakDown() {
                     variableName = this.id,
                     observationId = null,
                     plotId = null);
+        updateDropDownVar(this.id);
       })
       .transition()
       .duration(TIME)
@@ -462,6 +463,7 @@ function shapleyValues() {
                     variableName = this.id,
                     observationId = null,
                     plotId = null);
+        updateDropDownVar(this.id);
       })
       .transition()
       .duration(TIME)
@@ -708,6 +710,7 @@ function featureImportance() {
                     variableName = this.id,
                     observationId = null,
                     plotId = null);
+        updateDropDownVar(this.id);
       })
       .transition()
       .duration(TIME)
@@ -2658,4 +2661,11 @@ function generatePlots(arrPlotId) {
       mapIdPlotFunction[id]();
     }
   });
+}
+
+function updateDropDownVar(variableName) {
+  /// change dropdown variable on bar click
+  if (variableName == "prediction" || variableName == "intercept" ||
+      variableName == "other") { return; }
+  d3.select('#inputVar').property('value', variableName)
 }

### 2020-07-15 inst/d3js/modelStudio.js

@@ -169,6 +169,13 @@ initializeStudio();
 function initializeStudio() {
   /// this function initializes modelStudio (used only once, at start)
 
+  // center the ms
+  d3.select("#" + WIDGET_ID)
+    .style('position', 'absolute')
+    .style('left', 0)
+    .style('right', 0)
+    .style('margin', 'auto');
+
   // top decorations
   var TOP_G = svg.append("g")
                  .attr("class", "TOP_G");
@@ -187,20 +194,13 @@ function initializeStudio() {
        .attr("y2", studioMargin.top - margin.big);
 
   ///:\\\ add select observation input
-  let tempW = calculateTextWidth(dropDownData.map(e => e.text))*1.6 + 18; // 15px bold 600
-
-  // center the ms
-  d3.select("#" + WIDGET_ID)
-    .style('position', 'absolute')
-    .style('left', 0)
-    .style('right', 0)
-    .style('margin', 'auto');
+  let ddWidth = calculateTextWidth(dropDownData.map(e => e.text))*1.6 + 18; // 15px bold 600
 
   var input = d3.select("#" + WIDGET_ID)
                 .append("select")
-                .attr("id","input")
+                .attr("id", "input")
                 .style("position", "absolute") // to make input appear on top
-                .style("left", (studioWidth - margin.big - tempW)+"px")
+                .style("left", (studioWidth - margin.big - ddWidth)+"px")
                 .style("top", -studioHeight + 180)
                 .style("font-size", "15px")
                 .style("font-weight", 600)
@@ -222,6 +222,39 @@ function initializeStudio() {
     updatePlots(event = "observationChange",
                 variableName = null,
                 observationId = this.value,
+                plotId = null);
+  });
+  ///:\\\
+
+  ///:\\\ add select variable input
+  let ddWidthVar = calculateTextWidth(variableNames)*1.6 + 18; // 15px bold 600
+
+  var inputVar = d3.select("#" + WIDGET_ID)
+                   .append("select")
+                   .attr("id", "inputVar")
+                   .style("position", "absolute") // to make input appear on top
+                   .style("left", (studioWidth - margin.big - ddWidthVar - margin.big - ddWidth)+"px")
+                   .style("top", -studioHeight + 180)
+                   .style("font-size", "15px")
+                   .style("font-weight", 600)
+                   .style("color", "#371ea3");
+
+  inputVar.selectAll()
+          .data(variableNames)
+          .enter()
+          .append("option")
+          .attr("value", d => d)
[…]

### 2020-07-15 inst/doc/ms-r-python-examples.R

@@ -256,10 +256,10 @@ knitr::opts_chunk$set(
 #  library(reticulate)
 #  
 #  #! add blank create_architecture function before load !
-#  py_run_string("
+#  py_run_string('
 #  def create_architecture():
 #      return True
-#  ")
+#  ')
 #  
 #  explainer <- py_load_object("explainer_keras.pickle", pickle = "pickle")
 #  

### 2020-09-10 inst/doc/ms-perks-features.Rmd
version 2.0.0

@@
 
-`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces
-an interactive, customisable dashboard. It consists of multiple panels for plots with their short descriptions.
-Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for
-EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.
+The `modelStudio()` function computes various (instance and dataset level) model explanations 
+and produces a customisable dashboard, which consists of multiple panels for plots with their
+short descriptions. Easily save the dashboard and share it with others. Tools for
+[Explanatory Model Analysis](https://pbiecek.github.io/ema/) unite with tools for Exploratory Data Analysis 
+to give a broad overview of the model behavior.
 
@@
 
-`N` is a number of observations used for calculation of
+- `N` is a number of observations used for calculation of
 [Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
 and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
-`10*N` is a number of observations used for calculation of
+- `10*N` is a number of observations used for calculation of
 [Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
-`B` is a number of permutation rounds used for calculation of
+- `B` is a number of permutation rounds used for calculation of
 [Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
 [Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
+
 Decrease `N` and `B` parameters to lower the computation time or increase
@@
 Change `viewer` parameter to set where to display `modelStudio`.
-Best described in `r2d3` documentation:
-[`r2d3 viewer argument`](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).
+[Best described in `r2d3` documentation](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).
 
@@
 
-All options can be set outside of function call.
-More on that [here](https://github.com/berndbischl/parallelMap#being-lazy-configuration).
+All options can be set outside of the function call.
+[How to use parallelMap](https://github.com/mlr-org/parallelMap#being-lazy-configuration).
 
@@
 
-Customize some of `modelStudio` looks by overwriting default options returned
-by the `ms_options()` function. Full list of options:
-[documentation](http://modelstudio.drwhy.ai/reference/ms_options.html).
+Customize some of the `modelStudio` looks by overwriting default options returned
+by the `ms_options()` function.
+[Full list of options](https://modelstudio.drwhy.ai/reference/ms_options.html).
 
@@
 
+-------------------------------------------------------------------
+
+## Shiny
+
+Use the `widget_id` argument and `r2d3` package to render the `modelStudio` output in Shiny.
+See [Using r2d3 with Shiny](https://rstudio.github.io/r2d3/articles/shiny.html) and consider 
+the following example:
+
+```{r eval = FALSE}
+library(shiny)
+library(r2d3)
+
+ui <- fluidPage(
+  textInput("text", h3("Text input"), 
+            value = "Enter text..."),
+  uiOutput('dashboard')
+)
+
+server <- function(input, output) {
+  #:# id of div where modelStudio will appear
+  WIDGET_ID = 'MODELSTUDIO'
+
+  #:# create modelStudio 
+  library(modelStudio)
+  library(DALEX)
+  model <- glm(survived ~., data = titanic_imputed, family = "binomial")
+  explainer <- explain(model,
+                       data = titanic_imputed,
+                       y = titanic_imputed$survived,
+                       label = "Titanic GLM",
+                       verbose = FALSE)
+  ms <- modelStudio(explainer,
+                    widget_id = WIDGET_ID,  #:# use the widget_id 
+                    show_info = FALSE)    
+  ms$elementId <- NULL                      #:# remove elementId to stop the warning
+
+  #:# basic render d3 output
+  output[[WIDGET_ID]] <- renderD3({
+    ms
+  })
+
+  #:# use render ui to set proper width and height
+  output$dashboard <- renderUI({
+    d3Output(WIDGET_ID, width=ms$width, height=ms$height)
+  })
+}
+
+shinyApp(ui = ui, server = server)
+```
+
+-------------------------------------------------------------------
+
 ## DALEXtra
 
-Use `explain_*()` functions from the [DALEXtra](https://github.com/ModelOriented/DALEXtra)
-package to explain various models. Bellow basic example of making `modelStudio` for
-a `mlr` model using `explain_mlr()`.
+Use `explain_*()` functions from the [DALEXtra](https://github.com/ModelOriented/DALEXtra/)
+package to explain various models.
+
+Bellow basic example of making `modelStudio` for a `mlr` model using `explain_mlr()`.
 
@@
 
+-------------------------------------------------------------------
+
 ## References
 
-* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema)
+* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema/)
 * The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
-* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
+* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
 are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
-* Break Down and Shapley Values plots are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)
+* Break Down and Shapley Values explanations are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

### 2020-09-10 R/modelStudio.R

@@ -1,16 +1,28 @@
 #' @title Interactive Studio for Explanatory Model Analysis
 #'
 #' @description
-#' This function computes various (instance and dataset level) model explanations and produces an interactive,
-#' customisable dashboard. It consists of multiple panels for plots with their short descriptions.
-#' Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for
+#' This function computes various (instance and dataset level) model explanations and
+#' produces a customisable dashboard, which consists of multiple panels for plots with their
+#' short descriptions. Easily save the dashboard and share it with others. Tools for
+#' \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis} unite with tools for
 #' Exploratory Data Analysis to give a broad overview of the model behavior.
 #'
-#' Theoretical introduction to the plots:
-#' \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
+#' The extensive documentation covers:
+#'
+#' \itemize{
+#'   \item Function parameters description -
+#'  \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html}{\bold{perks and features}}
+#'   \item Framework and model compatibility -
+#'  \href{https://modelstudio.drwhy.ai/articles/ms-r-python-examples.html}{\bold{R & Python examples}}
+#'   \item Theoretical introduction to the plots -
+#'  \href{https://pbiecek.github.io/ema/}{Explanatory Model Analysis: Explore, Explain and Examine Predictive Models}
+#' }
 #'
 #' Displayed variable can be changed by clicking on the bars of plots or with the first dropdown list,
 #'  and observation can be changed with the second dropdown list.
+#' The dashboard gathers useful, but not sensitive, information about how it is being used (e.g. computation length,
+#'  package version, dashboard dimensions). This is for the development purposes only and can be blocked
+#'  by setting \code{telemetry} to \code{FALSE}.
 #'
 #' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
 #' @param new_observation New observations with columns that correspond to variables used in the model.
@@ -19,6 +31,7 @@
 #' @param time Time in ms. Set the animation length. Default is \code{500}.
 #' @param max_features Maximum number of features to be included in BD and SV plots.
[…]

### 2020-09-10 R/ms_options.R

@@ -33,7 +33,7 @@
 #' }
 #' \subsection{Plot specific options:}{
 #' \code{**} is a two letter code unique to each plot, might be
-#' one of \code{[bd,sv,cp,fi,pd,ad,fd,tv,at]}.\cr
+#' one of \code{[bd,sv,cp,fi,pd,ad,rv,fd,tv,at]}.\cr
 #'
 #' \describe{
 #' \item{**_title}{Plot specific title. Default varies.}
@@ -50,14 +50,15 @@
 #'
 #' \itemize{
 #'   \item The input object is implemented in \href{https://modeloriented.github.io/DALEX/}{\bold{DALEX}}
-#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
-#' are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
-#'   \item Break Down and Shapley Values plots are implemented in \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
+#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
+#'    are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
+#'   \item Break Down and Shapley Values explanations are implemented in
+#'    \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
 #' }
 #'
 #' @seealso
-#' Vignettes: \href{https://modeloriented.github.io/modelStudio/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
-#' and \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
+#' Vignettes: \href{https://modelstudio.drwhy.ai/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
+#' and \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
 #'
 #' @examples
 #' library("DALEX")
@@ -159,6 +160,10 @@ ms_options <- function(...) {
     ad_line_size = NULL,
     ad_bar_color = NULL,
     ad_line_color = NULL,
+    rv_title = "Residuals vs Feature",
+    rv_subtitle = NULL,
+    rv_point_size = NULL,
+    rv_point_color = NULL,
[…]

### 2020-09-10 R/ms_update_observations.R

@@ -2,7 +2,7 @@
 #'
 #' @description
 #' This function calculates local explanations on new observations and adds them
-#' to a \code{modelStudio} object.
+#' to the \code{modelStudio} object.
 #'
 #' @param object A \code{modelStudio} created with \code{modelStudio()}.
 #' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
@@ -15,8 +15,11 @@
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#more-calculations-means-more-time}{\bold{vignette}}
 #' @param show_info Verbose a progress on the console. Default is \code{TRUE}.
 #' @param parallel Speed up the computation using \code{parallelMap::parallelMap()}.
-#'  See \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html#parallel-computation}{\bold{vignette}}.
+#'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#parallel-computation}{\bold{vignette}}.
 #'  This might interfere with showing progress using \code{show_info}.
+#' @param widget_id Use an explicit element ID for the widget (rather than an automatically generated one).
+#'  Useful e.g. when using \code{modelStudio} with Shiny.
+#'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#shiny-1}{\bold{vignette}}.
 #' @param overwrite Overwrite existing observations and their explanations.
 #'  Default is \code{FALSE} which means add new observations to the existing ones.
 #' @param ... Other parameters.
@@ -27,14 +30,15 @@
 #'
 #' \itemize{
 #'   \item The input object is implemented in \href{https://modeloriented.github.io/DALEX/}{\bold{DALEX}}
-#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
-#' are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
-#'   \item Break Down and Shapley Values plots are implemented in \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
+#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
+#'    are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
+#'   \item Break Down and Shapley Values explanations are implemented in
[…]

### 2020-09-10 R/ms_update_options.R

@@ -16,14 +16,15 @@
 #'
 #' \itemize{
 #'   \item The input object is implemented in \href{https://modeloriented.github.io/DALEX/}{\bold{DALEX}}
-#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
-#' are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
-#'   \item Break Down and Shapley Values plots are implemented in \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
+#'   \item Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
+#'    are implemented in \href{https://modeloriented.github.io/ingredients/}{\bold{ingredients}}
+#'   \item Break Down and Shapley Values explanations are implemented in
+#'    \href{https://modeloriented.github.io/iBreakDown/}{\bold{iBreakDown}}
 #' }
 #'
 #' @seealso
-#' Vignettes: \href{https://modeloriented.github.io/modelStudio/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
-#' and \href{https://modeloriented.github.io/modelStudio/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
+#' Vignettes: \href{https://modelstudio.drwhy.ai/articles/ms-r-python-examples.html}{\bold{modelStudio - R & Python examples}}
+#' and \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html}{\bold{modelStudio - perks and features}}
 #'
 #' @examples
 #' library("DALEX")
@@ -38,7 +39,8 @@
 #'                              y = titanic_imputed$survived)
 #'
 #' # make a studio for the model
-#' ms <- modelStudio(explainer_titanic)
+#' ms <- modelStudio(explainer_titanic,
+#'                   N = 200,  B = 5) # faster example
 #'
 #' # update the options
 #' new_ms <- ms_update_options(ms,

### 2020-09-10 R/prepare.R

@@ -1,6 +1,6 @@
 prepare_break_down <- function(x, max_features = 10, baseline = NA, digits = 3,
-                               rounding_function = round, margin = 0.2) {
-  ### This function returns object needed to plot BreakDown in D3 ###
+                               rounding_function = round, margin = 0.2, ...) {
+  ### Return the object for the BreakDown plot ###
 
   if (is.null(x)) return(NULL)
 
@@ -37,7 +37,7 @@ prepare_break_down <- function(x, max_features = 10, baseline = NA, digits = 3,
 
 prepare_break_down_df <- function(x, max_features = 10, baseline = NA, digits = 3,
                                   rounding_function = round) {
-  ### This function returns data as DF needed to plot BreakDown in D3 ###
+  ### This function returns data as DF needed for the BreakDown plot ###
 
   # fix df
   x[,'variable'] <- as.character(x[,'variable'])
@@ -92,9 +92,11 @@ prepare_break_down_df <- function(x, max_features = 10, baseline = NA, digits = 
   x
 }
 
-prepare_shapley_values <- function(x, max_features = 10, show_boxplot = TRUE, baseline = NA,
-                                   digits = 3, rounding_function = round, margin = 0.15) {
-  ### This function returns object needed to plot ShapleyValues in D3 ###
+prepare_shapley_values <- function(x, max_features = 10, show_boxplot = TRUE,
+                                   baseline = NA,
+                                   digits = 3, rounding_function = round,
+                                   margin = 0.15, ...) {
+  ### Return the the object for the ShapleyValues plot ###
 
   if (is.null(x)) return(NULL)
   B <- NULL
@@ -115,17 +117,17 @@ prepare_shapley_values <- function(x, max_features = 10, show_boxplot = TRUE, ba
       variable_name = levels(as.factor(x_df$variable_name)),
       min = as.numeric(tapply(x_df$contribution, x_df$variable_name, min, na.rm = TRUE)),
       q1 = as.numeric(tapply(x_df$contribution, x_df$variable_name, quantile, 0.25, na.rm = TRUE)),
[…]

### 2020-09-10 inst/d3js/generatePlots.js

@@ -4,7 +4,7 @@
 // descriptions need to be IN plot functions because of tooltips
 
 /// initialize plots, select them if already there
-var BD, SV, CP, FI, PD, AD, FD, TV, AT;
+var BD, SV, CP, FI, PD, AD, RV, FD, TV, AT;
 
 /// later plot specific plotIds
 var mapIdPlotFunction = {};
@@ -68,6 +68,16 @@ if (svg.select("#AD").empty()) {
   AD = svg.select("#AD");
 }
 mapIdPlotFunction.AD = accumulatedDependence;
+
+if (svg.select("#RV").empty()) {
+  RV = svg.append("g")
+          .attr("class","plot")
+          .attr("id","RV")
+          .style("visibility", "hidden");
+} else {
+  RV = svg.select("#RV");
+}
+mapIdPlotFunction.RV = residualsVs;
 
 if (svg.select("#FD").empty()) {
   FD = svg.append("g")
@@ -380,7 +390,7 @@ function shapleyValues() {
   var y = d3.scaleBand()
             .rangeRound([margin.top - additionalHeight, margin.top + svPlotHeight])
             .padding(0.33)
-            .domain(bData.map(d => d.variable));
+            .domain(bData.map(d => d.variable_name));
 
   var xGrid = SV.append("g")
                 .attr("class", "grid")
@@ -440,7 +450,7 @@ function shapleyValues() {
 
   bars.append("rect")
       .attr("class", "SV-bars")
-      .attr("id", (d) => d.variable_name)
+      .attr("id", d => d.variable_name)
       .attr("fill", function(d) {
         switch (d.sign) {
           case "-1":
@@ -454,7 +464,7 @@ function shapleyValues() {
       .attr("fill-opacity", d => x(d.barSupport) - x(d.barStart) < 1.5
                                  ? 0 : 1) //invisible bar for clicking purpose
       .attr("x", d => d.contribution > 0 ? x(d.barStart) : x(d.barSupport))
-      .attr("y", d => y(d.variable))
+      .attr("y", d => y(d.variable_name))
       .attr("height", y.bandwidth())
       .on('mouseover', tooltip.show)
       .on('mouseout', tooltip.hide)
@@ -482,7 +492,7 @@ function shapleyValues() {
           .attr("class", "axisLabel")
           .attr("x", d => d.contribution > 0
                           ? x(d.barStart) - 5 : x(d.barSupport) + 5)
[…]

### 2020-09-10 inst/d3js/modelStudio.js

@@ -14,7 +14,8 @@ r2d3.onResize(function() {
 /// load all data
 var obsData = data[0],
     fiData = data[1], pdData = data[2],
-    adData = data[3], fdData = data[4],
+    adData = data[3], rvData = data[4],
+    fdData = data[4],
     tvData = data[4], atData = data[5];
 
 /// load options
@@ -22,10 +23,12 @@ var TIME = options.time,
     modelName = options.model_name,
     variableNames = options.variable_names,
     dim = options.facet_dim,
-    footerText = options.footer_text,
+    versionText = options.version_text,
+    measureText = options.measure_text,
     dropDownData = options.drop_down_data,
     EDA = options.eda,
     WIDGET_ID = options.widget_id,
+    IS_TARGET_BINARY = options.is_target_binary,
     SCALE_PLOT = options.scale_plot,
     SHOW_BOXPLOT = options.show_boxplot,
     SHOW_SUBTITLE = options.show_subtitle,
@@ -75,6 +78,10 @@ var TIME = options.time,
     adLineSize = options.ad_line_size || lineSize,
     adBarColor = options.ad_bar_color || barColor,
     adLineColor = options.ad_line_color || lineColor,
+    rvTitle = options.rv_title,
+    rvSubtitle = options.rv_subtitle || subTitle,
+    rvPointSize = options.rv_point_size || pointSize,
+    rvPointColor = options.tv_point_color || pointColor,
     fdTitle = options.fd_title,
     fdSubtitle = options.fd_subtitle || subTitle,
     fdBarWidth = options.fd_bar_width || barWidth,
@@ -90,7 +97,8 @@ var TIME = options.time,
     atPointSize = options.at_point_size || pointSize,
     atBarColor = options.at_bar_color || barColor,
     atLineColor = options.at_line_color || lineColor,
-    atPointColor = options.at_point_color || pointColor;
+    atPointColor = options.at_point_color || pointColor,
+    telemetry = options.telemetry;
 
 /// for observation choice
 var observationIds = Object.keys(obsData);
@@ -126,6 +134,7 @@ if (!SHOW_SUBTITLE) {
   fiSubtitle = null;
   pdSubtitle = null;
   adSubtitle = null;
+  rvSubtitle = null;
   fdSubtitle = null;
   tvSubtitle = null;
   atSubtitle = null;
@@ -133,16 +142,17 @@ if (!SHOW_SUBTITLE) {
 
 /// for plot chosing
 var notVisiblePlots = EDA ?
[…]

### 2020-09-10 inst/doc/ms-perks-features.R

@@ -140,6 +140,48 @@ knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 #  new_ms
 
 ## ----eval = FALSE-------------------------------------------------------------
+#  library(shiny)
+#  library(r2d3)
+#  
+#  
+#  ui <- fluidPage(
+#    textInput("text", h3("Text input"),
+#              value = "Enter text..."),
+#    uiOutput('dashboard')
+#  )
+#  
+#  server <- function(input, output) {
+#    #:# id of div where modelStudio will appear
+#    WIDGET_ID = 'MODELSTUDIO'
+#  
+#    #:# create modelStudio
+#    library(modelStudio)
+#    library(DALEX)
+#    model <- glm(survived ~., data = titanic_imputed, family = "binomial")
+#    explainer <- explain(model,
+#                         data = titanic_imputed,
+#                         y = titanic_imputed$survived,
+#                         label = "Titanic GLM",
+#                         verbose = FALSE)
+#    ms <- modelStudio(explainer,
+#                      widget_id = WIDGET_ID,  #:# use the widget_id
+#                      show_info = FALSE)
+#    ms$elementId <- NULL                      #:# remove elementId to stop the warning
+#  
+#    #:# basic render d3 output
+#    output[[WIDGET_ID]] <- renderD3({
+#      ms
+#    })
+#  
+#    #:# use render ui to set proper width and height
+#    output$dashboard <- renderUI({
+#      d3Output(WIDGET_ID, width=ms$width, height=ms$height)
+#    })
+#  }
+#  
+#  shinyApp(ui = ui, server = server)
+
+## ----eval = FALSE-------------------------------------------------------------
 #  library(DALEXtra)
 #  library(mlr)
 #  

### 2020-09-10 inst/doc/ms-r-python-examples.R

@@ -8,13 +8,9 @@ knitr::opts_chunk$set(
 )
 
 ## ----eval = FALSE-------------------------------------------------------------
-#  # packages for explainer objects
+#  # packages for the explainer objects
 #  install.packages("DALEX")
 #  install.packages("DALEXtra")
-#  
-#  # update main dependencies
-#  install.packages("ingredients")
-#  install.packages("iBreakDown")
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # load packages and data
@@ -211,9 +207,9 @@ knitr::opts_chunk$set(
 #  
 #  # fit a model
 #  model <- rand_forest() %>%
-#    set_engine("ranger", importance = "impurity") %>%
-#    set_mode("regression") %>%
-#    fit(m2.price ~ ., data = train)
+#           set_engine("ranger", importance = "impurity") %>%
+#           set_mode("regression") %>%
+#           fit(m2.price ~ ., data = train)
 #  
 #  # create an explainer for the model
 #  explainer <- explain(model,
@@ -224,13 +220,53 @@ knitr::opts_chunk$set(
 #  # make a studio for the model
 #  modelStudio(explainer)
 
+## ----eval=FALSE---------------------------------------------------------------
+#  # load packages and data
+#  library(tidymodels)
+#  library(DALEXtra)
+#  library(modelStudio)
+#  
+#  data <- DALEX::titanic_imputed
+#  
+#  # split the data
+#  index <- sample(1:nrow(data), 0.7*nrow(data))
+#  train <- data[index,]
+#  test <- data[-index,]
+#  
+#  # tidymodels fit takes target as factor
+#  train$survived <- as.factor(train$survived)
+#  
+#  # fit a model
+#  rec <- recipe(survived ~ ., data = train) %>%
+#         step_normalize(fare)
+#  
+#  clf <- rand_forest(mtry = 2) %>%
+#         set_engine("ranger") %>%
+#         set_mode("classification")
+#  
+#  wflow <- workflow() %>%
+#           add_recipe(rec) %>%
+#           add_model(clf)
+#  
+#  model <- wflow %>% fit(data = train)
+#  
+#  # create an explainer for the model
+#  explainer <- explain_tidymodels(model,
+#                                  data = test,
+#                                  y = test$survived,
+#                                  label = "tidymodels")
+#  
+#  # pick observations
+#  new_observation <- test[1:2,]
+#  rownames(new_observation) <- c("id1", "id2")
+#  
+#  # make a studio for the model
[…]

### 2020-09-10 tests/testthat/test_2_0.R

@@ -1,0 +1,96 @@
+context("Test v2.0.0")
+
+set.seed(1313)
+v <- FALSE
+
+data_multiclass <- DALEX::HR[1:100,]
+model_multiclass <- ranger::ranger(status ~. ,
+                                   data = data_multiclass,
+                                   probability = TRUE)
+exp_multiclass <- DALEX::explain(model_multiclass,
+                                 data = data_multiclass,
+                                 y = data_multiclass$status,
+                                 verbose = v)
+
+data_fifa <- DALEX::fifa[1:100, 1:10]
+model_fifa <- ranger::ranger(value_eur ~. ,
+                             data_fifa)
+exp_fifa <- DALEX::explain(model_fifa,
+                           data = data_fifa,
+                           y = data_fifa$value_eur,
+                           verbose = v)
+
+#:# errors #:#
+exp_nodata <- DALEX::explain(model_fifa, verbose = v)
+exp_noy <- DALEX::explain(model_fifa, data = data_fifa, verbose = v)
+
+testthat::expect_error(modelStudio::modelStudio(exp_multiclass))
+testthat::expect_error(modelStudio::modelStudio(exp_nodata))
+testthat::expect_error(modelStudio::modelStudio(exp_noy))
+
+#:# new functionalities #:#
+case1 <- testthat::expect_silent(
+  modelStudio::modelStudio(exp_fifa, data_fifa[1,],
+                           widget_id = "MS", telemetry = F,
+                           N = 5, B = 2, show_info = v))
+
+testthat::expect_true(case1$elementId == 'MS')
+testthat::expect_true(!isTRUE(case1$x$options$telemetry))
+
+case2 <- testthat::expect_silent(
+  modelStudio::modelStudio(exp_fifa, data_fifa[1:2,],
+                           max_vars = 5, rounding_funtion = signif,
+                           digits = 3,
+                           N = 5, B = 2, show_info = v))
+testthat::expect_true(
+  all(c("mse:", "rmse:", "r2:", "mad:") %in%
+        strsplit(case2$x$options$measure_text, split=" ")[[1]]))
+
+#:# test NA #:#
+
+data_na <- DALEX::fifa[1:100, 2:10]
+model_na <- ranger::ranger(value_eur~., data_na)
+data_na[1:10,] <- NA
+
+pf <- function(model, data) {
+  data <- impute(data)
+  predict(model, data)$predictions
+}
+
[…]

### 2020-09-10 tests/testthat/test_modelStudio.R

@@ -2,99 +2,79 @@ context("Check modelStudio() function")
 
 source("test_objects.R")
 
+N = 10
+B = 2
+
 ms1 <- testthat::expect_silent(modelStudio::modelStudio(explain_glm,
                                                         new_observation = titanic_test[1,-9],
                                                         show_info = v))
 
-# ms2 <- modelStudio::modelStudio(model_glm,
-#                    max_features = 5,
-#                    data = titanic_test[,-9],
-#                    y = titanic_test$survived == "yes",
-#                    new_observation = titanic_test[1:2,-9],
-#                    N = 50, B = 10,
-#                    show_info = v)
-#
-# ms3 <- modelStudio::modelStudio(model_glm,
-#                    max_features = 5,
-#                    facet_dim = c(2,3),
-#                    N = 150,
-#                    B = 10,
-#                    time = 900,
-#                    data = titanic_test[,-9],
-#                    y = titanic_test$survived == "yes",
-#                    label = "xxx",
-#                    new_observation = titanic_test[1:10,-9],
-#                    show_info = v)
-
 ms4 <- testthat::expect_silent(modelStudio::modelStudio(explain_glm_numerical,
                                                         new_observation = titanic_test[1:2, c(2,6,7,8)],
-                                                        N = 50, B = 10,
+                                                        N = N, B = B,
                                                         show_info = v))
 
 ms5 <- testthat::expect_silent(modelStudio::modelStudio(explain_glm_not_numerical,
                                                         new_observation = titanic_test[1:2, c(1,3,4,5)],
-                                                        N = 50, B = 10,
+                                                        N = N, B = B,
                                                         show_info = v))
 
 ms6 <- testthat::expect_silent(modelStudio::modelStudio(explain_model_small,
                                                         new_observation = titanic_test[1:2, c(1,2)],
-                                                        N = 50, B = 10,
+                                                        N = N, B = B,
                                                         show_info = v))
 
 ms_readme <-  testthat::expect_silent(modelStudio::modelStudio(explain_titanic_glm,
                                                                new_observations,
-                                                               facet_dim = c(2,2), N = 200, B = 20, time = 0,
+                                                               facet_dim = c(2,2),
+                                                               N = N, B = B, time = 0,
                                                                show_info = v))
 
 ms_rf_apartments <- testthat::expect_silent(modelStudio::modelStudio(explain_rf,
                                                                      new_observation = apartments[1:2,-1],
[…]

### 2020-11-22 inst/doc/ms-perks-features.Rmd
version 2.1.0

@@
 
+If `new_observation = NULL`, then choose `new_observation_n` observations, evenly spread by the order of `y_hat`.
+This shall always include the observations, which ids are `which.min(y_hat)` and `which.max(y_hat)`.
+
+```{r eval = FALSE}
+modelStudio(explainer, new_observation_n = 5) # default is 3
+```
+
 ### grid size
@@
 [Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
-and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
-- `10*N` is a number of observations used for calculation of
-[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
+and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles (default is `300`). 
+- `N_fi` is a number of observations used for calculation of
+[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `10*N`).
 - `B` is a number of permutation rounds used for calculation of
-[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
-[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
+[Shapley Values](https://pbiecek.github.io/ema/shapley.html) (default is `10`).
+- `B_fi` is a number of permutation rounds used for calculation of
+[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `B`).
 
@@
   model <- glm(survived ~., data = titanic_imputed, family = "binomial")
-  explainer <- explain(model,
+  explainer <- DALEX::explain(model,
                               data = titanic_imputed,

### 2020-11-22 R/modelStudio.R

@@ -27,18 +27,19 @@
 #' @param explainer An \code{explainer} created with \code{DALEX::explain()}.
 #' @param new_observation New observations with columns that correspond to variables used in the model.
 #' @param new_observation_y True label for \code{new_observation} (optional).
+#' @param new_observation_n Number of observations to be taken from the \code{explainer$data} if \code{new_observation = NULL}.
+#'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#instance-explanations}{\bold{vignette}}
 #' @param facet_dim Dimensions of the grid. Default is \code{c(2,2)}.
 #' @param time Time in ms. Set the animation length. Default is \code{500}.
 #' @param max_features Maximum number of features to be included in BD and SV plots.
 #'  Default is \code{10}.
 #' @param max_vars An alias for \code{max_features}. If provided, it will override the value.
-#' @param N Number of observations used for the calculation of PD and AD.
-#'  \code{10*N} is a number of observations used for the calculation of FI.
-#'  Default \code{N} is \code{300}.
+#' @param N Number of observations used for the calculation of PD and AD. Default is \code{300}.
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#more-calculations-means-more-time}{\bold{vignette}}
-#' @param B Number of permutation rounds used for calculation of SV and FI.
-#'  Default is \code{10}.
+#' @param N_fi Number of observations used for the calculation of FI. Default is \code{10*N}.
+#' @param B Number of permutation rounds used for calculation of SV. Default is \code{10}.
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#more-calculations-means-more-time}{\bold{vignette}}
+#' @param B_fi Number of permutation rounds used for calculation of FI. Default is \code{B}.
 #' @param eda Compute EDA plots and Residuals vs Feature plot, which adds the data to the dashboard. Default is \code{TRUE}.
 #' @param show_info Verbose a progress on the console. Default is \code{TRUE}.
 #' @param parallel Speed up the computation using \code{parallelMap::parallelMap()}.
@@ -52,6 +53,8 @@
 #' @param widget_id Use an explicit element ID for the widget (rather than an automatically generated one).
 #'  Useful e.g. when using \code{modelStudio} with Shiny.
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#shiny-1}{\bold{vignette}}.
[…]

### 2020-11-22 inst/d3js/modelStudio.js

@@ -34,6 +34,7 @@ var TIME = options.time,
     SHOW_SUBTITLE = options.show_subtitle,
     subTitle = options.subtitle || modelName,
     msTitle = options.ms_title,
+    msSubtitle = options.ms_subtitle,
     barWidth = options.bar_width,
     lineSize = options.line_size,
     pointSize = options.point_size,
@@ -98,7 +99,8 @@ var TIME = options.time,
     atBarColor = options.at_bar_color || barColor,
     atLineColor = options.at_line_color || lineColor,
     atPointColor = options.at_point_color || pointColor,
-    telemetry = options.telemetry;
+    telemetry = options.telemetry,
+    license = options.license;
 
 /// for observation choice
 var observationIds = Object.keys(obsData);
@@ -120,7 +122,7 @@ var w = options.w, h = options.h;
 var plotWidth = w + margin.left + margin.right,
     plotHeight = h + margin.top + margin.bottom;
 
-var studioMargin = {top: 50, bottom: 50},
+var studioMargin = {top: options.ms_margin_top, bottom: options.ms_margin_bottom},
     studioWidth = dim[1]*plotWidth,
     studioHeight = studioMargin.top + dim[0]*plotHeight + studioMargin.bottom;
 
@@ -173,6 +175,7 @@ for (let i = 0; i < dim[0]; i++) {
 }
 
 ///:\\\
+if (license) document.head.appendChild(document.createComment(license));
 if (telemetry) startTelemetrySession();
 initializeStudio();
 ///:\\\
@@ -196,6 +199,15 @@ function initializeStudio() {
        .attr("x", 15)
        .attr("y", 30)
        .text(msTitle);
+
+  if (msSubtitle !== null) {
+      TOP_G.append("text")
+           .attr("class", "subTitle")
+           .attr("x", 15)
+           .attr("y", 40)
+           .text(msSubtitle)
+           .call(wrapText, studioWidth - 15);
+  }
 
   TOP_G.append("line")
        .attr("class", "mainLine")

### 2020-11-22 inst/doc/ms-perks-features.R

@@ -44,6 +44,9 @@ knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 #              new_observation_y  = true_labels)
 
 ## ----eval = FALSE-------------------------------------------------------------
+#  modelStudio(explainer, new_observation_n = 5) # default is 3
+
+## ----eval = FALSE-------------------------------------------------------------
 #  # small dashboard with 2 panels
 #  modelStudio(explainer,
 #              facet_dim = c(1,2))
@@ -158,11 +161,11 @@ knitr::kable(head(train), digits = 2, caption = "DALEX::HR dataset")
 #    library(modelStudio)
 #    library(DALEX)
 #    model <- glm(survived ~., data = titanic_imputed, family = "binomial")
-#    explainer <- explain(model,
-#                         data = titanic_imputed,
-#                         y = titanic_imputed$survived,
-#                         label = "Titanic GLM",
-#                         verbose = FALSE)
+#    explainer <- DALEX::explain(model,
+#                                data = titanic_imputed,
+#                                y = titanic_imputed$survived,
+#                                label = "Titanic GLM",
+#                                verbose = FALSE)
 #    ms <- modelStudio(explainer,
 #                      widget_id = WIDGET_ID,  #:# use the widget_id
 #                      show_info = FALSE)

### 2020-11-22 inst/doc/ms-r-python-examples.R

@@ -41,8 +41,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer,
-#              new_observation)
+#  modelStudio(explainer, new_observation)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # load packages and data
@@ -77,8 +76,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer,
-#              new_observation)
+#  modelStudio(explainer, new_observation)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # load packages and data
@@ -112,8 +110,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer,
-#              new_observation,
+#  modelStudio(explainer, new_observation,
 #              options = ms_options(margin_left = 140))
 
 ## ----eval = FALSE-------------------------------------------------------------
@@ -147,8 +144,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer,
-#              new_observation)
+#  modelStudio(explainer, new_observation)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # load packages and data
@@ -185,8 +181,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer,
-#              new_observation,
+#  modelStudio(explainer, new_observation,
 #              B = 5)
 #  
 #  # shutdown h2o
@@ -261,8 +256,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer,
-#              new_observation)
+#  modelStudio(explainer, new_observation)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # package for pickle load

### 2021-01-07 inst/doc/ms-perks-features.Rmd
version 2.1.1

@@
 short descriptions. Easily save the dashboard and share it with others. Tools for
-[Explanatory Model Analysis](https://pbiecek.github.io/ema/) unite with tools for Exploratory Data Analysis 
+[Explanatory Model Analysis](https://ema.drwhy.ai/) unite with tools for Exploratory Data Analysis 
 to give a broad overview of the model behavior.
@@
 Pass data points to the `new_observation` parameter for instance explanations
-such as [Break Down](https://pbiecek.github.io/ema/breakDown.html),
-[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
-[Ceteris Paribus](https://pbiecek.github.io/ema/ceterisParibus.html) Profiles.
+such as [Break Down](https://ema.drwhy.ai/breakDown.html),
+[Shapley Values](https://ema.drwhy.ai/shapley.html) and
+[Ceteris Paribus](https://ema.drwhy.ai/ceterisParibus.html) Profiles.
 Use `new_observation_y` to show their true labels.
@@
 - `N` is a number of observations used for calculation of
-[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
-and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles (default is `300`). 
+[Partial Dependence](https://ema.drwhy.ai/partialDependenceProfiles.html)
+and [Accumulated Dependence](https://ema.drwhy.ai/accumulatedLocalProfiles.html) Profiles (default is `300`). 
 - `N_fi` is a number of observations used for calculation of
-[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `10*N`).
+[Feature Importance](https://ema.drwhy.ai/featureImportance.html) (default is `10*N`).
 - `B` is a number of permutation rounds used for calculation of
-[Shapley Values](https://pbiecek.github.io/ema/shapley.html) (default is `10`).
+[Shapley Values](https://ema.drwhy.ai/shapley.html) (default is `10`).
 - `B_fi` is a number of permutation rounds used for calculation of
-[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `B`).
+[Feature Importance](https://ema.drwhy.ai/featureImportance.html) (default is `B`).
 
@@
 
-* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema/)
+* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain, and Examine Predictive Models.](https://ema.drwhy.ai/)
 * The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)

### 2021-01-07 inst/doc/ms-r-python-examples.Rmd
version 2.1.1

@@
 ```{r eval = FALSE}
-# packages for explainer objects
+# packages for the explainer objects
 install.packages("DALEX")
 install.packages("DALEXtra")
-
-# update main dependencies
-install.packages("ingredients")
-install.packages("iBreakDown")
 ```
 
-### mlr [dashboard](https://modeloriented.github.io/modelStudio/mlr.html)
+### mlr [dashboard](https://modelstudio.drwhy.ai/mlr.html)
 
@@
 # make a studio for the model
-modelStudio(explainer,
-            new_observation)
+modelStudio(explainer, new_observation)
 ```
 
-### mlr3 [dashboard](https://modeloriented.github.io/modelStudio/mlr3.html)
+### mlr3 [dashboard](https://modelstudio.drwhy.ai/mlr3.html)
 
@@
 # make a studio for the model
-modelStudio(explainer,
-            new_observation)
+modelStudio(explainer, new_observation)
 ```
 
-### xgboost [dashboard](https://modeloriented.github.io/modelStudio/xgboost.html)
+### xgboost [dashboard](https://modelstudio.drwhy.ai/xgboost.html)
 
@@
 # make a studio for the model
-modelStudio(explainer,
-            new_observation,
+modelStudio(explainer, new_observation,
             options = ms_options(margin_left = 140))
@@
 
-### caret [dashboard](https://modeloriented.github.io/modelStudio/caret.html)
+### caret [dashboard](https://modelstudio.drwhy.ai/caret.html)
 
@@
 # make a studio for the model
-modelStudio(explainer,
-            new_observation)
+modelStudio(explainer, new_observation)
 ```
 
-### h2o [dashboard](https://modeloriented.github.io/modelStudio/h2o.html)
+### h2o [dashboard](https://modelstudio.drwhy.ai/h2o.html)
 
@@
 # make a studio for the model
-modelStudio(explainer,
-            new_observation,
+modelStudio(explainer, new_observation,
             B = 5)
@@
 
-### parsnip [dashboard](https://modeloriented.github.io/modelStudio/parsnip.html)
+### parsnip [dashboard](https://modelstudio.drwhy.ai/parsnip.html)
 
@@
 
+### tidymodels [dashboard](https://modelstudio.drwhy.ai/tidymodels.html)
+
+In this example we will make a studio for the `ranger` model on `titanic` data.
+
+```{r eval=FALSE}
+# load packages and data
+library(tidymodels)
+library(DALEXtra)
+library(modelStudio)
+
+data <- DALEX::titanic_imputed
+
+# split the data
+index <- sample(1:nrow(data), 0.7*nrow(data))
+train <- data[index,]
+test <- data[-index,]
+
+# tidymodels fit takes target as factor
+train$survived <- as.factor(train$survived)
+
+# fit a model
+rec <- recipe(survived ~ ., data = train) %>%
+       step_normalize(fare)
+
+clf <- rand_forest(mtry = 2) %>%
+       set_engine("ranger") %>%
+       set_mode("classification")
+
+wflow <- workflow() %>%
+         add_recipe(rec) %>%
+         add_model(clf)
+
+model <- wflow %>% fit(data = train)
+
+# create an explainer for the model
+explainer <- explain_tidymodels(model,
+                                data = test,
+                                y = test$survived,
+                                label = "tidymodels")
+
+# pick observations
+new_observation <- test[1:2,]
+rownames(new_observation) <- c("id1", "id2")
+
+# make a studio for the model
+modelStudio(explainer, new_observation)
+```
+
 ## Python
@@
 ```{bash, eval=FALSE, engine="sh"}
-# package for Explainer object
-pip3 install dalex --force
+# package for the Explainer object
+pip install dalex -U
 ```
@@
 install.packages("reticulate")
-
-# update main dependencies
-install.packages("ingredients")
-install.packages("iBreakDown")
 ```
 
-### scikit-learn [dashboard](https://modeloriented.github.io/modelStudio/scikitlearn.html)
+### scikit-learn [dashboard](https://modelstudio.drwhy.ai/scikitlearn.html)
 
@@
 
-### lightGBM [dashboard](https://modeloriented.github.io/modelStudio/lightgbm.html)
+### lightgbm [dashboard](https://modelstudio.drwhy.ai/lightgbm.html)
 
@@
 # create an explainer for the model
-explainer = dx.Explainer(model, data=X_test, y=y_test, label='lightGBM')
+explainer = dx.Explainer(model, data=X_test, y=y_test, label='lightgbm')
 
@@
 
-### keras/tensorflow [dashboard](https://modeloriented.github.io/modelStudio/keras.html)
+### keras/tensorflow [dashboard](https://modelstudio.drwhy.ai/keras.html)
 
@@
 #! add blank create_architecture function before load !
-py_run_string("
+py_run_string('
 def create_architecture():
     return True
-")
+')
 
@@
 
+-------------------------------------------------------------------
+
 ## References
 
-* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema)
+* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain, and Examine Predictive Models.](https://ema.drwhy.ai/)
 * The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
-* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
+* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
 are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
-* Break Down and Shapley Values plots are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)
+* Break Down and Shapley Values explanations are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

### 2021-07-13 R/modelStudio.R
version 3.0.0

@@ -37,11 +37,13 @@
 #' @param N Number of observations used for the calculation of PD and AD. Default is \code{300}.
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#more-calculations-means-more-time}{\bold{vignette}}
 #' @param N_fi Number of observations used for the calculation of FI. Default is \code{10*N}.
+#' @param N_sv Number of observations used for the calculation of SV. Default is \code{3*N}.
 #' @param B Number of permutation rounds used for calculation of SV. Default is \code{10}.
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#more-calculations-means-more-time}{\bold{vignette}}
 #' @param B_fi Number of permutation rounds used for calculation of FI. Default is \code{B}.
 #' @param eda Compute EDA plots and Residuals vs Feature plot, which adds the data to the dashboard. Default is \code{TRUE}.
 #' @param show_info Verbose a progress on the console. Default is \code{TRUE}.
+#' @param verbose An alias for \code{show_info}. If provided, it will override the value.
 #' @param parallel Speed up the computation using \code{parallelMap::parallelMap()}.
 #'  See \href{https://modelstudio.drwhy.ai/articles/ms-perks-features.html#parallel-computation}{\bold{vignette}}.
 #'  This might interfere with showing progress using \code{show_info}.
@@ -148,6 +150,7 @@
 #'   explainer_HR <- explain(model_HR,
 #'                           data = HR_matrix,
 #'                           y = HR$status == "fired",
+#'                           type = "classification",
 #'                           label = "xgboost")
 #'
 #'   # pick observations
@@ -177,6 +180,7 @@ modelStudio.explainer <- function(explainer,
                                   max_features = 10,
                                   N = 300,
                                   N_fi = N*10,
+                                  N_sv = N*3,
                                   B = 10,
                                   B_fi = B,
                                   eda = TRUE,
@@ -188,6 +192,7 @@ modelStudio.explainer <- function(explainer,
                                   license = NULL,
                                   telemetry = TRUE,
                                   max_vars = NULL,
+                                  verbose = NULL,
                                   ...) {
 
   start_time <- Sys.time()
@@ -203,6 +208,7 @@ modelStudio.explainer <- function(explainer,
[…]

### 2021-07-13 R/ms_options.R

@@ -113,7 +113,7 @@ ms_options <- function(...) {
     margin_top = 50,
     margin_right = 20,
     margin_bottom = 70,
-    margin_left = 105,
+    margin_left = NULL, # 105,
     margin_inner = 40,
     margin_small = 5,
     margin_big = 10,
@@ -194,11 +194,12 @@ ms_options <- function(...) {
   default_options
 }
 
-#' deprecated since v1.1
+#' deprecated since v1.1 (May 2020)
+#' removed in v2.2 (July 2021)
 #' @export
 #' @rdname ms_options
-modelStudioOptions <- function(...) {
-  warning("The 'modelStudioOptions()' function is deprecated; use 'ms_options()' instead.")
-  ret <- ms_options(...)
-  ret
-}
+# modelStudioOptions <- function(...) {
+#   warning("The 'modelStudioOptions()' function is deprecated; use 'ms_options()' instead.")
+#   ret <- ms_options(...)
+#   ret
+# }

### 2021-07-13 inst/d3js/modelStudio.js

@@ -111,11 +111,16 @@ var CLICKED_VARIABLE_NAME = variableNames[0],
     IS_BUTTON_CLICKED = false;
 
 /// set dimensions
-var margin = {top: options.margin_top, right: options.margin_right,
-              bottom: options.margin_bottom, left: options.margin_left,
-              inner: options.margin_inner,
-              small: options.margin_small, big: options.margin_big,
-              ytitle: options.margin_ytitle};
+var margin = {
+  top: options.margin_top,
+  right: options.margin_right,
+  bottom: options.margin_bottom,
+  left: options.margin_left,
+  inner: options.margin_inner,
+  small: options.margin_small,
+  big: options.margin_big,
+  ytitle: options.margin_ytitle
+};
 
 var w = options.w, h = options.h;
 
@@ -490,7 +495,7 @@ function initializeStudio() {
 
   if (facetData.length >= 1) {
     svg.selectAll('.enterChoiceButton').filter('#enterChoiceButton0').dispatch('click');
-    svg.select("#chosePlotButton0").select("#BD").dispatch('click');
+    svg.select("#chosePlotButton0").select("#FI").dispatch('click');
   }
 
   if (facetData.length >= 2) {

### 2021-07-13 inst/doc/ms-r-python-examples.R

@@ -103,6 +103,7 @@ knitr::opts_chunk$set(
 #  explainer <- explain(model,
 #                       data = test_matrix,
 #                       y = test$survived,
+#                       type = "classification",
 #                       label = "xgboost")
 #  
 #  # pick observations
@@ -110,8 +111,7 @@ knitr::opts_chunk$set(
 #  rownames(new_observation) <- c("id1", "id2")
 #  
 #  # make a studio for the model
-#  modelStudio(explainer, new_observation,
-#              options = ms_options(margin_left = 140))
+#  modelStudio(explainer, new_observation)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # load packages and data
@@ -269,8 +269,7 @@ knitr::opts_chunk$set(
 #  
 #  # make a studio for the model
 #  library(modelStudio)
-#  modelStudio(explainer, B = 5,
-#              options = ms_options(margin_left = 160))
+#  modelStudio(explainer, B = 5)
 
 ## ----eval = FALSE-------------------------------------------------------------
 #  # load the explainer from the pickle file

### 2021-07-13 inst/doc/ms-rmarkdown.R

@@ -1,0 +1,21 @@
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo = TRUE)
+
+## ----warning = FALSE, message = FALSE-----------------------------------------
+library("DALEX")
+library("ranger")
+library("modelStudio")
+
+# fit a model
+model <- ranger(score ~., data = happiness_train)
+
+# create an explainer for the model    
+explainer <- explain(model,
+                     data = happiness_test,
+                     y = happiness_test$score,
+                     label = "Random Forest",
+                     verbose = FALSE)
+
+# make a studio for the model
+modelStudio(explainer)
+

### 2021-07-13 tests/testthat/test_warnings_and_errors.R

@@ -20,11 +20,19 @@ if (requireNamespace("xgboost", quietly=TRUE)) {
   })
 }
 
-testthat::test_that("deprecated modelStudioOptions", {
-  testthat::expect_warning(
+# deprecated since v1.1 (May 2020)
+# removed in v2.2 (July 2021)
+# testthat::test_that("deprecated modelStudioOptions", {
+#   testthat::expect_warning(
+#     ms <- modelStudio::modelStudioOptions()
+#   )
+# })
+testthat::test_that("removed modelStudioOptions", {
+  testthat::expect_error(
     ms <- modelStudio::modelStudioOptions()
   )
 })
+
 
 if (requireNamespace("ranger", quietly=TRUE)) {
   ms <- modelStudio::modelStudio(explain_rf, apartments[1:2,], N = 5, B = 2, show_info = v)
